---
title: "Analysis pipeline for the behavioral and functional MRI data from the semantic Mnemonic Similarity Task"
output: html_document
editor_options:
  chunk_output_type: console
---
# Glossary & packages

ENC = Encoding task phase
REC = Recognition task phase
RS = repetition suppression (first presentation - repeat)
PS = pattern separation (hippocampal operation)
MD = mnemonic discrimination (behavioural correlate)
LDI = lure discrimination index (proxy of MD)

```{r}
knitr::opts_chunk$set(echo = TRUE)

library(ppcor)
library(tidyverse)
library(tidytuesdayR)
library(readxl)
library(tidyr)
library(scales)
library(ggplot2)
library(psycho)
library(ggpubr)
library(rstatix)
library(afex)
library(MuMIn)
library(lme4)
library(lmerTest)
library(ggstatsplot)
library(sjPlot)
library(smplot2)
library(openxlsx)
library(stats)
library(performance)
library(emmeans)
library(purrr)
library(broom)
library(ggpattern)
library(ggtext)
library(dplyr)
library(ppcor)
library(readr)
library(stringr)
library(grid)
library(gridExtra)
library(gtable)
library(patchwork)

theme_set(theme_light())

custom_theme = theme(
      plot.title = element_text(color="black", size=30, face="bold",  hjust = 0, vjust = 3), #30 for covariate plots
      axis.text.x = element_text(vjust = 0.5, hjust=0.5, size = 20, face="bold"), #was 16 for other plots besides rec resp rate
      axis.text.y = element_text(vjust = 0.5, hjust=0.5, size = 20, face="bold"),
      axis.title.x = element_text(vjust = -2, hjust=0.5, size = 26, face="bold"),
      axis.title.y = element_text(vjust = 3, hjust=0.5, size = 26, face="bold"),
      legend.text = element_text(vjust = 0.5, hjust=0.5, size = 22, face="bold"),
      legend.title = element_text(vjust = 0.5, hjust=0.5, size = 24, face="bold"),
      strip.text = element_text(vjust = 0.5, hjust=0.5, size = 22, face="bold"),
      plot.margin = margin(30, 30, 30, 30),
      panel.grid.major = element_blank(), 
      panel.grid.minor = element_blank(),
      panel.background = element_blank(), 
      axis.line = element_line(colour = "black")
      )


```


# Data handling

## Read-in MR

```{r}

semmst_mr_data = read.xlsx("./data/fmri/ses-01/subfield_data_featquery_2025.xlsx")

```

## Preprocess MR

```{r}

semmst_mr_data_filtered = semmst_mr_data %>%
  dplyr::select(-c(cope_num, query_type, groupanalysis_type)) %>% 
  dplyr::rename(ID = subject) %>% 
  mutate(
    ID = as.factor(ID),
    space_type = as.factor(space_type),
    task = as.factor(task),
    cope_name = as.factor(cope_name),
    hemisphere = as.factor(hemisphere),
    roi = as.factor(roi),
    mask_type = as.factor(mask_type),
    contrast = as.factor(contrast),
    cluster = as.factor(cluster),
    estimate = as.numeric(estimate),
  )

```


## Read-in behavior

```{r}

semmst_behav_data <- read_xlsx("./data/behavioural/smst/smst_mr_behvaioural_grand.xlsx")

```

## Preprocess behavior

```{r}

# Clean and factorize
semmst_behav_data_filtered <- semmst_behav_data %>%
  dplyr::rename(ID = participant_id) %>%
  mutate(ID = factor(str_c("sub-", ID)),
         task = factor(task, levels = c("enc", "rec")),
         run = factor(run),
         trial_type = factor(trial_type),
         stim_file = factor(stim_file),
         itemno = factor(itemno),
         order = factor(order),
         response = tolower(response),
         sex = factor(sex, levels = c("male", "female")),
         handedness = factor(handedness, levels = "R"),
         response_time = as.numeric(response_time),
         onset = as.numeric(onset),
         correctness = factor(correctness)) %>% 
  filter(ID %in% semmst_mr_data_filtered$ID)

semmst_mr_behav_data_enc <- semmst_behav_data_filtered %>% 
  filter(task == "enc",
         trial_type != "FILLER") %>% 
  mutate(former_type = ifelse(trial_type=="REPEAT", "TARGET", "LURE")) %>%
  dplyr::select(ID, noun, former_type) %>% 
  distinct() 

semmst_mr_behav_data_rec <- semmst_behav_data_filtered %>% 
  filter(task == "rec",
         !is.na(response)) %>% 
  left_join(semmst_mr_behav_data_enc, by = c("ID", "noun") ) %>% 
  mutate(response = factor(response, levels=c("old", "new"))) %>% 
  mutate(trial_type = factor(trial_type)) %>% 
  mutate(former_type = factor(former_type)) %>% 
  mutate(correctness = factor(correctness, levels=c(0,1)))

```

### LDI

```{r}
semmst_behav_data_rec_filtered = semmst_mr_behav_data_rec %>% 
  filter(task == "rec") %>%
  filter(response != "None") %>% 
  mutate(response = as.factor(response))

semmst_behav_data_rec_wide_dprime = semmst_behav_data_rec_filtered %>% 
  dplyr::count(ID, trial_type, response) %>% 
  unite("trial_resp", c("trial_type", "response"), sep = "_") %>% 
  spread(trial_resp, n) %>% 
  mutate_at(vars(matches("_")), ~ifelse(is.na(.), 0, .)) %>% 
  mutate(targ_n = TARGET_new + TARGET_old) %>% 
  mutate(close_n = CLOSE_new + CLOSE_old) %>% 
  mutate(distant_n = DISTANT_new + DISTANT_old) %>% 
  mutate(foil_n = FOIL_new + FOIL_old) %>% 
  mutate(LURE_old = CLOSE_old + DISTANT_old) %>% 
  mutate(LURE_new = CLOSE_new + DISTANT_new) %>% 
  mutate(lure_n = LURE_new + LURE_old)

# Simple recognition - TARG vs FOIL  
rec_dprime <- psycho::dprime(
  n_hit = semmst_behav_data_rec_wide_dprime$TARGET_old,
  n_fa = semmst_behav_data_rec_wide_dprime$FOIL_old,
  n_miss = semmst_behav_data_rec_wide_dprime$TARGET_new,
  n_cr = semmst_behav_data_rec_wide_dprime$FOIL_new,
  n_targets = semmst_behav_data_rec_wide_dprime$targ_n,
  n_distractors = semmst_behav_data_rec_wide_dprime$foil_n,
  adjusted = TRUE
)

# Close lure discrimination - TARG vs CLOSE  
close_dprime <- psycho::dprime(
  n_hit = semmst_behav_data_rec_wide_dprime$TARGET_old,
  n_fa = semmst_behav_data_rec_wide_dprime$CLOSE_old,
  n_miss = semmst_behav_data_rec_wide_dprime$TARGET_new,
  n_cr = semmst_behav_data_rec_wide_dprime$CLOSE_new,
  n_targets = semmst_behav_data_rec_wide_dprime$targ_n,
  n_distractors = semmst_behav_data_rec_wide_dprime$close_n,
  adjusted = TRUE
)

# Distant lure discrimination - TARG vs DISTANT  
dist_dprime <- psycho::dprime(
  n_hit = semmst_behav_data_rec_wide_dprime$TARGET_old,
  n_fa = semmst_behav_data_rec_wide_dprime$DISTANT_old,
  n_miss = semmst_behav_data_rec_wide_dprime$TARGET_new,
  n_cr = semmst_behav_data_rec_wide_dprime$DISTANT_new,
  n_targets = semmst_behav_data_rec_wide_dprime$targ_n,
  n_distractors = semmst_behav_data_rec_wide_dprime$distant_n,
  adjusted = TRUE
)

# All lure discrimination - TARG vs LURE  
lure_dprime <- psycho::dprime(
  n_hit = semmst_behav_data_rec_wide_dprime$TARGET_old,
  n_fa = semmst_behav_data_rec_wide_dprime$LURE_old,
  n_miss = semmst_behav_data_rec_wide_dprime$TARGET_new,
  n_cr = semmst_behav_data_rec_wide_dprime$LURE_new,
  n_targets = semmst_behav_data_rec_wide_dprime$targ_n,
  n_distractors = semmst_behav_data_rec_wide_dprime$lure_n,
  adjusted = TRUE
)


semmst_behav_data_rec_summary <- semmst_behav_data_rec_wide_dprime %>% 
  transmute(
    ID,
    
    # Recognition
    rec_dprime     = rec_dprime$dprime,
    rec_correct    = (TARGET_old) / (targ_n),
    rec_incorrect  = (TARGET_new) / (targ_n),
    
    # Close LDI
    close_dprime   = close_dprime$dprime,
    close_correct  = (CLOSE_new) / (close_n),
    close_incorrect= (CLOSE_old) / (close_n),
    
    # Distant LDI
    distant_dprime = dist_dprime$dprime,
    distant_correct  = (DISTANT_new) / (distant_n),
    distant_incorrect= (DISTANT_old) / (distant_n),
    
    # Lure LDI
    lure_dprime = lure_dprime$dprime,
    lure_correct  = (LURE_new) / (lure_n),
    lure_incorrect= (LURE_old) / (lure_n),
  )

```

## Merge

```{r}

semmst_merged_data <- semmst_mr_data_filtered %>%
  left_join(
    semmst_behav_data_filtered %>%
      dplyr::select(ID, sex:GRO_score_SES02) %>%
      distinct(ID, .keep_all = TRUE),
    by = "ID"
  ) %>%
  left_join(semmst_behav_data_rec_summary, by = "ID") %>% 
  droplevels()

```

## FILTER for HYPOTHESIS TESTING

```{r}

# REPETITION SENSTIVITY
semmst_merged_data_filtered = semmst_merged_data %>% 
  filter(contrast %in% c("ENC_ERP_ALLRS")) %>% 
  filter(space_type == "standard") %>% 
  filter(voxels > 50) %>% 
  filter(as.numeric(as.character(cluster)) < 140) %>% 
  mutate(roi_cluster = paste(hemisphere, roi, cluster, sep = "_")) %>% 
  mutate(roi_hemisphere = paste(hemisphere, roi, sep = "_")) %>%
  mutate(Vocabulary_scale = scale(Vocabulary)) %>% 
  mutate(Digit_Symbol_scale = scale(Digit_Symbol)) %>% 
  mutate(NonWord_sum_scale = scale(NonWord_sum)) 

# ANATOMY CONTROL
semmst_merged_data_filtered_anat = semmst_merged_data %>% 
  filter(contrast %in% c("anatHC")) %>% 
  mutate(roi_cluster = paste(hemisphere, roi, cluster, sep = "_")) %>% 
  mutate(roi_hemisphere = paste(hemisphere, roi, sep = "_")) %>%
  mutate(Vocabulary_scale = scale(Vocabulary)) %>% 
  mutate(Digit_Symbol_scale = scale(Digit_Symbol)) %>% 
  mutate(NonWord_sum_scale = scale(NonWord_sum)) 

```


# Results
## Analysis 1 - Behavioural

### ANOVA on LDI

```{r}

semmst_behav_data_rec_LDI_ANCOVA = semmst_behav_data_rec_LDI_ANOVA %>% 
  left_join(semmst_behav_data_rec_filtered %>%  dplyr::select(ID, age, sex, education, Vocabulary, Digit_Symbol, NonWord_sum) %>% distinct(), by="ID") %>%
  mutate(Vocabulary_scale = scale(Vocabulary)) %>% 
  mutate(Digit_Symbol_scale = scale(Digit_Symbol)) %>% 
  mutate(NonWord_sum_scale = scale(NonWord_sum)) %>% drop_na()
 
# ASSUMPTION CHECKS
## OUTLIER
semmst_behav_data_rec_LDI_ANCOVA %>%
  group_by(dprime_type) %>%
  identify_outliers(dprime_value)

##NORMALITY
semmst_behav_data_rec_LDI_ANCOVA %>% 
  group_by(dprime_type) %>%
  shapiro_test(dprime_value) %>%  print(n=40)

ggqqplot(semmst_behav_data_rec_LDI_ANCOVA, "dprime_value", ggtheme = theme_bw()) +
  facet_grid(. ~ dprime_type, labeller = "label_both")

# ANCOVA
ANCOVA_behav_data_rec_LDI = semmst_behav_data_rec_LDI_ANCOVA %>%
  anova_test(dv = dprime_value, wid = ID, within = c(dprime_type), covariate = c(sex, age, Vocabulary_scale, Digit_Symbol_scale, NonWord_sum_scale))

get_anova_table(ANCOVA_behav_data_rec_LDI)

# REPORT
## dprime_type                   174.597      <0.001 ***  0.582000
## NonWord_sum_scale               8.346      0.008  **   0.229000
## Digit_Symbol_scale:dprime_type  3.593      0.035  *    0.028000

```

### GLMEM: semantic similarity ~ response

```{r}

semmst_behav_data_rec_filtered_GLMEM <- semmst_behav_data_rec_filtered %>%
  mutate(across(all_of(c("Vocabulary", "Digit_Symbol", "NonWord_sum", "arousal", "concreteness", "imageability", "meaningfulness")),
                ~ as.numeric(scale(.x)),           # drop scale() attributes
                .names = "{.col}_scale")) %>% 
  drop_na(Vocabulary) %>% 
  mutate(response = relevel(response, ref = "new"))

semmst_behav_data_rec_filtered_GLMEM_lure = semmst_behav_data_rec_filtered_GLMEM %>% 
  filter(trial_type %in% c("CLOSE", "DISTANT"))

model_simple_cont = glmer(response ~ cosine * trial_type * former_type +
                                (1|ID) + 
                                (1|itemno),
                                family = binomial("probit"), 
                                data = semmst_behav_data_rec_filtered_GLMEM_lure,
                                control = glmerControl(optimizer ='bobyqa', optCtrl=list(maxfun = 20000)), nAGQ=0)

model_complex_cont = glmer(response ~ cosine * trial_type * former_type +
                                        age + sex + education + Vocabulary_scale + Digit_Symbol_scale +
                                                  NonWord_sum_scale + arousal_scale + meaningfulness_scale + concreteness_scale +
                                        (1|ID) + 
                                        (1|itemno),
                                        family = binomial("probit"), 
                                        data = semmst_behav_data_rec_filtered_GLMEM_lure,
                                        control = glmerControl(optimizer ='bobyqa', optCtrl=list(maxfun = 20000)), nAGQ=0)

anova(model_simple_cont, model_complex_cont)
summary(model_complex_cont)
confint(model_complex_cont, parm="beta_", method="Wald")


# REPORT                                       Estimate Std. Error z value Pr(>|z|)      2.5 %      97.5 % (Intercept)                               
## cosine                                      5.131681   1.806091   2.841  0.00449 ** -7.444086424 -0.35150302
## NonWord_sum_scale                          -0.213690   0.069192  -3.088  0.00201 ** -0.349304360 -0.07807487
## meaningfulness_scale                        0.145144   0.073066   1.986  0.04698 *  0.001936827  0.28835127
## trial_typeDISTANT                           2.011234   1.931225   1.041  0.29768   
## former_typeTARGET                          -1.376078   1.970692  -0.698  0.48501 

```

## Analysis 2 - ENC RS

### ANOVA - REPEAT vs. LURE

```{r}
# FILTER DATA
semmst_merged_data_H1 = semmst_merged_data_filtered %>% 
  filter(task == "Encoding") %>% 
  filter(cope_name %in% c("LureFirst", "ExactFirst", "LureRepeat", "ExactRepeat")) %>% 
  extract(
    col = cope_name,
    into = c("stim_type", "order"),
    regex = "([A-Za-z]+?)(First|Repeat)$"
  ) %>% 
  mutate(
    stim_type = as.factor(stim_type),
    order = as.factor(order)
  ) %>% 
  mutate(stim_type = factor(stim_type, levels = c("Exact", "Lure")))

# ASSUMPTION CHECKS
## OUTLIER
semmst_merged_data_H1 %>%
  group_by(stim_type, order, roi_cluster) %>%
  identify_outliers(estimate) %>% 
  dplyr::select(ID, is.outlier, is.extreme) %>% 
  filter(is.extreme==TRUE)

semmst_merged_data_H1_nooutlier = semmst_merged_data_H1 %>%
  group_by(stim_type, order, roi_cluster) %>%
  filter(! ID %in% c("sub-434971")) %>%  #, " sub-012421", "sub-632012", "sub-800472")) %>% # c("sub-434971", "sub-982347")) %>%
  drop_na(NonWord_sum_scale) %>% 
  ungroup()

##NORMALITY
semmst_merged_data_H1_nooutlier %>% 
  group_by(stim_type, order) %>%
  shapiro_test(estimate)

# ANOVA
semmst_merged_data_H1_nooutlier_AOV = semmst_merged_data_H1_nooutlier %>%
  anova_test(dv = estimate, wid = ID, within = c(stim_type, order, roi_cluster), covariate = c(NonWord_sum_scale, Digit_Symbol_scale))

get_anova_table(semmst_merged_data_H1_nooutlier_AOV)

# REPORT                       Effect DFn DFd      F        p p<.05      ges
## 3                                       stim_type   1  25 16.271 4.54e-04     * 4.50e-02
## 4                                           order   1  25 50.948 1.76e-07     * 1.41e-01
## 4                                 stim_type:order   1  25 12.810 1.00e-03     * 3.20e-02
## 6                               order:roi_cluster   1  25  5.677 2.50e-02     * 6.00e-03
# COVARIATES
## 16             Digit_Symbol_scale:stim_type:order   1  25  6.123 2.00e-02     * 1.60e-02
## 19            NonWord_sum_scale:order:roi_cluster   1  25  9.266 5.00e-03     * 1.00e-02


# POST-HOC
# pairwise comparisons - stim_type * order
semmst_merged_data_H1_nooutlier_PWC = semmst_merged_data_H1_nooutlier %>%
  drop_na(Digit_Symbol) %>% 
  group_by(stim_type) %>% 
  pairwise_t_test(
    estimate ~ order, 
    paired = TRUE,
    detailed = TRUE,
    ) %>% 
  ungroup() %>% 
#  group_by(stim_type) %>%
  adjust_pvalue(method = "bonferroni") %>%
  add_significance() %>%
  ungroup() %>% 
  mutate(label = paste0("p=", signif(p.adj, 3)))
semmst_merged_data_H1_nooutlier_PWC

# REPORT        estimate .y.      group1 group2    n1    n2 statistic        p    df conf.low conf.high method alternative    p.adj p.adj.signif label 
## Exact       0.190  estimate First  Repeat    56    56      8.86 3.52e-12    55   0.147      0.232 T-test two.sided   7.04e-12 ****         p=7.04e-12
## Lure        0.0720 estimate First  Repeat    56    56      3.44 1   e- 3    55   0.0301     0.114 T-test two.sided   2   e- 3 **           p=0.002 

# pairwise comparisons - order * roi_cluster
semmst_merged_data_H1_nooutlier_PWC = semmst_merged_data_H1_nooutlier %>%
  drop_na(Digit_Symbol) %>% 
  group_by(order) %>% 
  pairwise_t_test(
    estimate ~ stim_type, 
    paired = TRUE,
    detailed = TRUE,
    ) %>% 
  ungroup() %>% 
#  group_by(stim_type) %>%
  adjust_pvalue(method = "bonferroni") %>%
  add_significance() %>%
  ungroup() %>% 
  mutate(label = paste0("p=", signif(p.adj, 3)))
semmst_merged_data_H1_nooutlier_PWC

# REPORT        estimate .y.      group1 group2    n1    n2 statistic          p    df conf.low conf.high method alternative      p.adj p.adj.signif labe 
## First   -0.0114 estimate Exact  Lure      56    56    -0.734 0.466         55  -0.0427    0.0198 T-test two.sided   0.932      ns           p=0.932   
## Repeat  -0.129  estimate Exact  Lure      56    56    -5.45  0.00000124    55  -0.176    -0.0815 T-test two.sided   0.00000248 ****         p=2.48e-06

```



### ANOVA - REPEAT vs. LURE and CORRECT vs. INCORRECT

For subsequent correctness we use those models, where only those runs were included, where non-zero amount of trials were in each bin.

```{r}

semmst_merged_data_filtered_subseq = semmst_merged_data_filtered %>%
  dplyr::filter(task %in% c("EncodingSubseq", "EncodingSubseq_limited")) %>%
  dplyr::group_by(ID) %>%
  dplyr::filter(
    task == "EncodingSubseq" &
      !any(task == "EncodingSubseq_limited")
  ) %>%
  dplyr::ungroup()

semmst_merged_data_HE = semmst_merged_data_filtered_subseq %>% 
  filter(cope_name %in% c("CorrectExactRepeat", "CorrectExactFirst", "CorrectLureRepeat", "CorrectLureFirst", "IncorrectExactFirst", "IncorrectExactRepeat", "IncorrectLureFirst", "IncorrectLureRepeat"))


```


```{r}

# STANDARD
semmst_merged_data_HE_test = semmst_merged_data_HE %>%
  extract(col = cope_name,
          into = c("correctness", "stim_type", "order"),
          regex = "^(Correct|Incorrect)(Exact|Lure)(First|Repeat)$") %>% 
  mutate(
    stim_type = as.factor(stim_type),
    order = as.factor(order)
  ) %>% 
  mutate(stim_type = factor(stim_type, levels = c("Exact", "Lure"))) %>% 
  mutate(correctness = factor(correctness, levels = c("Correct", "Incorrect"))) %>% 
  droplevels() 

# ASSUMPTION CHECKS
## OUTLIER
semmst_merged_data_HE_test %>%
  group_by(order, correctness, roi_cluster) %>%
  identify_outliers(estimate) %>% 
  dplyr::select(ID, roi_cluster, stim_type, order, correctness, is.outlier, is.extreme) %>% 
  filter(is.extreme == TRUE)

semmst_merged_data_HE_test_nooutlier = semmst_merged_data_HE_test %>% 
  #filter(!ID %in% c("sub-434971")) %>%  #, "sub-124846")) %>%  #c("sub-434971", "sub-632012", "sub-680997")) %>%  #, "sub-193800")) %>% 
  ungroup()

##NORMALITY
semmst_merged_data_HE_test_nooutlier %>% 
  group_by(stim_type, order, correctness, roi, hemisphere) %>%
  shapiro_test(estimate) %>%  print(n=100)

# ANOVA
semmst_merged_data_HE_test_AOV = semmst_merged_data_HE_test_nooutlier %>% 
  anova_test(dv = estimate, wid = ID, within = c(stim_type, correctness, order, roi_cluster))#, covariate = c(NonWord_sum_scale))

get_anova_table(semmst_merged_data_HE_test_AOV)

# REPORT
## 1                                stim_type   1  28 13.459000 1.00e-03     * 1.80e-02
## 3                                    order   1  28 43.614000 3.66e-07     * 4.60e-02
## 6                          stim_type:order   1  28  7.165000 1.20e-02     * 1.50e-02
## 7                        correctness:order   1  28  0.048000 8.28e-01       1.18e-04
## 11             stim_type:correctness:order   1  28  0.277000 6.03e-01       4.92e-04

# POST-HOC
# pairwise comparisons
semmst_merged_data_HE_test_nooutlier_PWC = semmst_merged_data_HE_test_nooutlier %>%
  group_by(stim_type) %>% 
  pairwise_t_test(
    estimate ~ order, 
    paired = TRUE,
    detailed = TRUE,
    ) %>%
  adjust_pvalue(method = "bonferroni") %>%
  add_significance() %>%
  ungroup() %>% 
  mutate(label = paste0("p=", signif(p.adj, 3)))
semmst_merged_data_HE_test_nooutlier_PWC %>% dplyr::select(-c(alternative, method, .y., )) %>%  print(n=50)

# REPORT stim_type estimate group1 group2    n1    n2 statistic             p    df conf.low conf.high        p.adj p.adj.signif label     
## 1 Exact       0.164  First  Repeat   116   116      6.32 0.00000000513   115  0.112      0.215  0.0000000103 ****         p=1.03e-08
## 2 Lure        0.0454 First  Repeat   116   116      1.72 0.088           115 -0.00681    0.0975 0.176        ns           p=0.176  

```


## Analysis 3 - Power function

### CLOSE vs DISTANT

```{r}
# FILTER DATA
semmst_merged_data_H1b = semmst_merged_data_filtered %>% 
  filter(task == "Encoding") %>% 
  filter(cope_name %in% c("CloseRepeat", "DistantRepeat"))

# ASSUMPTION CHECKS
## OUTLIER
semmst_merged_data_H1b %>%
  group_by(cope_name, roi_cluster) %>%
  identify_outliers(estimate) %>% 
  dplyr::select(ID, is.outlier, is.extreme) %>% 
  filter(is.extreme==TRUE)

semmst_merged_data_H1b_nooutlier = semmst_merged_data_H1b %>%
  group_by(cope_name, roi_cluster) %>%
  filter(! ID %in% c("sub-434971")) %>%  #, " sub-012421", "sub-632012", "sub-800472")) %>% # c("sub-434971", "sub-982347")) %>%
  ungroup()

##NORMALITY
semmst_merged_data_H1b_nooutlier %>% 
  group_by(cope_name) %>%
  shapiro_test(estimate)

# ANOVA
semmst_merged_data_H1b_nooutlier_AOV = semmst_merged_data_H1b_nooutlier %>%
  anova_test(dv = estimate, wid = ID, within = c(cope_name, roi_cluster), covariate = c(NonWord_sum_scale, Digit_Symbol_scale))

get_anova_table(semmst_merged_data_H1b_nooutlier_AOV)

# REPORT                       Effect DFn DFd      F        p p<.05      ges
## 1             cope_name   1  28 0.111 0.742       7.47e-04
## 2           roi_cluster   1  28 0.011 0.917       9.52e-05
## 3 cope_name:roi_cluster   1  28 0.077 0.784       3.99e-04

```


### POWER CURVE vs LINEAR

Prepare data - export to MATLAB to use Curve Fitting Toolbox

```{r}
# FILTER DATA
semmst_merged_data_H1_clodis_powerfunc = semmst_merged_data_filtered %>% 
  filter(task == "EncodingFirst") %>% 
  filter(cope_name %in% c("AllFirst", "CloseRepeat", "DistantRepeat", "ExactRepeat")) %>% 
  mutate(roi_cluster = paste(hemisphere, roi, cluster, sep = "_")) %>% 
  mutate(roi_hemisphere = paste(hemisphere, roi, sep = "_")) %>% 
  mutate(cope_name = factor(cope_name, levels = c("ExactRepeat", "CloseRepeat", "DistantRepeat", "AllFirst"))) %>% 
  mutate(roi_cluster = factor(roi_cluster))

# OUTLIER
semmst_merged_data_H1_clodis_powerfunc %>%
  group_by(cope_name, roi_cluster) %>%
  identify_outliers(estimate) %>% 
  dplyr::select(ID, is.outlier, is.extreme) 

semmst_merged_data_H1_clodis_powerfunc_nooutlier = semmst_merged_data_H1_clodis_powerfunc 

## EXPORT TO MATLAB
export_matlab <- semmst_merged_data_H1_clodis_powerfunc_nooutlier %>%
  filter(cope_name %in% c("AllFirst","ExactRepeat","CloseRepeat","DistantRepeat")) %>%
  transmute(
    Subj = ID,
    ROI  = as.character(roi_cluster),
    Cond = as.character(cope_name),
    Beta = estimate
  )

write.csv(export_matlab, "derivatives/transfer_raw_matlab.csv", row.names = FALSE)

```

The rest of this analysis is in "scripts/smst_mr1_powerfunction.m"

## Analysis 4 - ENC RS ~ LDI

### Prepare bias scores

```{r}
group_vars_H3 <- c("ID", "mask_type", "space_type", "contrast", "roi_cluster")

# baseline
semmst_merged_data_H3_neural_ps = semmst_merged_data_filtered %>% 
  filter(task %in% c("Encoding")) %>% 
  filter(cope_name %in% c("ExactFirst", "ExactRepeat", "LureFirst","LureRepeat", "CloseFirst", "CloseRepeat", "DistantFirst", "DistantRepeat")) %>% 
  dplyr::select(ID, space_type, cope_name, hemisphere, roi, mask_type, cluster, voxels, contrast, task, roi_cluster, roi_hemisphere, estimate, NonWord_sum_scale, Digit_Symbol_scale, rec_dprime:lure_incorrect) %>% 
  group_by(across(all_of(group_vars_H3))) %>%
  pivot_wider(names_from = cope_name, values_from = estimate, values_fill = NA_real_) %>%
  mutate(
    # --- Non-RS bias scores (Exact denominator) ---
    LureBiasScore      = LureRepeat - ExactRepeat, 
    CloseBiasScore     = CloseRepeat - ExactRepeat,
    DistantBiasScore   = DistantRepeat - ExactRepeat
  ) %>%
  ungroup()

```

### Correlation - LURES

```{r}

# 1) Filter / define roi_group
df_corr_input_all <- semmst_merged_data_H3_neural_ps %>%
  mutate(roi_group = roi_cluster) %>%
  dplyr::select(
    ID, roi_group, roi, hemisphere, cluster, voxels,
    LureBiasScore, lure_dprime,
    NonWord_sum_scale, Digit_Symbol_scale
  ) %>%
  ungroup()

# 2) Mahalanobis outlier detection (per ROI)
alpha <- 0.99  # cutoff for chi-square (df=2)

md_tbl_all <- df_corr_input_all %>%
  dplyr::group_by(roi_group) %>%
  dplyr::group_modify(~{
    d <- .x %>% dplyr::select(ID, LureBiasScore, lure_dprime) %>% tidyr::drop_na()
    if (nrow(d) < 3) {
      return(tibble::tibble(ID = character(), MD = numeric(), p = numeric(),
                            cutoff = numeric(), is_outlier = logical()))
    }
    X <- as.matrix(d[, c("LureBiasScore", "lure_dprime")])
    center <- colMeans(X)
    covmat <- stats::cov(X)
    md <- stats::mahalanobis(X, center = center, cov = covmat)
    tibble::tibble(
      ID = d$ID,
      MD = md,
      p  = 1 - stats::pchisq(md, df = 2),
      cutoff = stats::qchisq(alpha, df = 2),
      is_outlier = md > stats::qchisq(alpha, df = 2)
    )
  }) %>%
  ungroup()

md_outliers_all <- md_tbl_all %>% dplyr::filter(is_outlier)
md_multi_all    <- md_outliers_all %>% dplyr::count(ID, sort = TRUE) %>% dplyr::filter(n > 1)

md_tbl_all
md_outliers_all
md_multi_all

# 3) Remove outlier ID
df_corr_input_all_nooutlier <- df_corr_input_all %>%
  dplyr::filter(ID != "sub-434971") %>%
  droplevels() %>%
  ungroup()

# 4) Fisher-z CI for Pearson r (95% hard-coded)
pearson_ci <- function(r, n) {
  z <- atanh(r)
  se <- 1 / sqrt(n - 3)
  zcrit <- stats::qnorm(1 - (1 - 0.95) / 2)
  c(low = tanh(z - zcrit * se), high = tanh(z + zcrit * se))
}

# 5) SIMPLE correlations only (Pearson) per ROI + Bonferroni
H3_corr_lure_simple <- df_corr_input_all_nooutlier %>%
  dplyr::group_by(roi_group) %>%
  dplyr::group_modify(~{
    d <- .x %>% dplyr::select(LureBiasScore, lure_dprime) %>% tidyr::drop_na()
    ct <- stats::cor.test(d$LureBiasScore, d$lure_dprime, method = "pearson")
    r  <- unname(ct$estimate)
    p  <- ct$p.value
    n  <- nrow(d)
    ci <- pearson_ci(r, n)

    tibble::tibble(
      n = n,
      r = r,
      p = p,
      ci = sprintf("[%.3f, %.3f]", ci["low"], ci["high"])
    )
  }) %>%
  ungroup() %>%
  mutate(
    p_adj = p.adjust(p, method = "bonferroni")
  ) %>%
  arrange(p_adj)

H3_corr_lure_simple


```

### Compare correlations

```{r}
# --- A) Build subject-level wide table (bias per ROI, plus lure_dprime per ID)
wide_bias <- df_corr_input_all_nooutlier %>%
  group_by(ID, roi_group) %>%
  summarise(
    bias = mean(LureBiasScore, na.rm = TRUE),
    lure_dprime = first(lure_dprime),
    .groups = "drop"
  ) %>%
  tidyr::pivot_wider(
    names_from  = roi_group,
    values_from = bias,
    names_repair = "minimal"
  )

roi_cols <- setdiff(names(wide_bias), c("ID", "lure_dprime"))

# --- B) Pairwise dependent-correlation tests:
# compares r(lure_dprime, ROI1_bias) vs r(lure_dprime, ROI2_bias)
H3_pairwise_roi_corrdiff <- combn(roi_cols, 2, simplify = FALSE) %>%
  purrr::map_dfr(function(pair){
    roi1 <- pair[1]
    roi2 <- pair[2]

    d <- wide_bias %>%
      select(lure_dprime, all_of(roi1), all_of(roi2)) %>%
      drop_na()

    n <- nrow(d)

    r1  <- cor(d$lure_dprime, d[[roi1]], method = "pearson")
    r2  <- cor(d$lure_dprime, d[[roi2]], method = "pearson")
    r12 <- cor(d[[roi1]], d[[roi2]], method = "pearson")

    # Williams/Steiger-style test for two dependent correlations sharing one variable
    tst <- psych::r.test(n = n, r12 = r1, r13 = r2, r23 = r12)

    tibble(
      roi1 = roi1,
      roi2 = roi2,
      n = n,
      r_roi1 = r1,
      r_roi2 = r2,
      r_roi1_roi2 = r12,
      t = unname(tst$t),
      p = unname(tst$p)
    )
  }) %>%
  mutate(p_adj_bonf = p.adjust(p, method = "bonferroni")) %>%
  arrange(p_adj_bonf, p)

H3_pairwise_roi_corrdiff
```


## Analysis 5 - REC MD

### ANOVA #1 - LureMD

```{r}
### FILTERING FR AT LEAST 5 items per condition per run
run_status <- semmst_behav_data_rec_filtered %>% 
  select(ID, run, trial_type, correctness) %>% 
  filter(trial_type %in% c("CLOSE", "DISTANT")) %>%
  mutate(run = as.integer(str_extract(as.character(run), "\\d+"))) %>%
  count(ID, run, correctness, name = "n") %>%
  group_by(ID, run) %>%
  complete(correctness, fill = list(n = 0)) %>%
  summarise(
    min_n = min(n),                 
    run_ok = (min_n >= 5),
    .groups = "drop"
  ) %>%
  select(ID, run, run_ok) %>% 
  tidyr::pivot_wider(
    names_from  = run,
    values_from = run_ok,
    names_prefix = "run",
    values_fill = FALSE
  ) %>%
  mutate(
    group = case_when(
      run1 & run2 ~ "both_ok",
      !run1 & run2 ~ "run1_low_only",
      run1 & !run2 ~ "run2_low_only",
      TRUE ~ "both_low"
    )
  )

# We use both runs only if both have n > 5 items in all bins, otherwise only 1 run or exclude
ids_both_ok      <- run_status %>% filter(group == "both_ok")      %>% pull(ID)
ids_run1_lowonly <- run_status %>% filter(group == "run1_low_only") %>% pull(ID)
ids_run2_lowonly <- run_status %>% filter(group == "run2_low_only") %>% pull(ID)

semmst_merged_data_filtered_lures = semmst_merged_data_filtered

df_LureCR_all <- semmst_merged_data_filtered_lures %>%
  filter(task == "RecognitionRespAll", cope_name == "LureCR")

df_LureFA_both_ok <- semmst_merged_data_filtered_lures %>%
  filter(task == "RecognitionRespAll", cope_name == "LureFA") %>%
  semi_join(tibble(ID = ids_both_ok), by = "ID")

df_LureFA_use_run2 <- semmst_merged_data_filtered_lures %>%
  filter(task == "RecognitionRespAllRun2", cope_name == "LureFA") %>%
  semi_join(tibble(ID = ids_run1_lowonly), by = "ID")

df_LureFA_use_run1 <- semmst_merged_data_filtered_lures %>%
  filter(task == "RecognitionRespAllRun1", cope_name == "LureFA") %>%
  semi_join(tibble(ID = ids_run2_lowonly), by = "ID")

# Merge for testing
df_LureFA_all <- bind_rows(
  df_LureFA_both_ok,
  df_LureFA_use_run2,
  df_LureFA_use_run1
)

semmst_merged_data_H4_lureFACR <- bind_rows(df_LureCR_all, df_LureFA_all)

keep_ids <- semmst_merged_data_H4_lureFACR %>%
  group_by(ID, roi_cluster) %>%
  summarise(
    has_LureCR = any(cope_name == "LureCR"),
    has_LureFA = any(cope_name == "LureFA"),
    .groups = "drop"
  ) %>%
  filter(has_LureCR & has_LureFA) %>% count(ID) %>% 
  filter(n > 1) %>% 
  pull(ID)

semmst_merged_data_H4_lureFACR <- semmst_merged_data_H4_lureFACR %>%
  filter(ID %in% keep_ids) %>% 
  droplevels()

  
# ASSUMPTION CHECKS
## OUTLIER
semmst_merged_data_H4_lureFACR %>%
  group_by(cope_name, roi_cluster, task) %>%
  identify_outliers(estimate) %>% 
  dplyr::select(ID, roi_cluster, cope_name, is.outlier, is.extreme) %>% 
  filter(is.extreme==TRUE)

semmst_merged_data_H4_lureFACR_nooutlier = semmst_merged_data_H4_lureFACR %>%
  #filter(ID != "sub-632012") %>% 
  ungroup()

semmst_merged_H4_AOV = semmst_merged_data_H4_lureFACR_nooutlier %>% 
  droplevels() %>%
  anova_test(dv = estimate, wid = ID, within = c(cope_name, roi_cluster))#, covariate = c(NonWord_sum_scale))

get_anova_table(semmst_merged_H4_AOV)

# REPORT                 Effect DFn DFd     F     p p<.05   ges
## 1               cope_name   1  23 1.621 0.216       0.013
## 2             roi_cluster   1  23 0.584 0.453       0.005
## 3   cope_name:roi_cluster   1  23 1.079 0.310       0.006

# POST-HOC
# pairwise comparisons - stim_type * order
semmst_merged_H4_REC_lureFACR_PWC = semmst_merged_data_H4_lureFACR_nooutlier %>%
  group_by(roi_cluster) %>% 
  pairwise_t_test(
    estimate ~ cope_name, 
    paired = TRUE,
    detailed = TRUE,
    ) %>% 
  ungroup() %>% 
  adjust_pvalue(method = "bonferroni") %>%
  add_significance() %>%
  ungroup() %>% 
  mutate(label = paste0("p=", signif(p.adj, 3)))
semmst_merged_H4_REC_lureFACR_PWC

```

### ANOVA #2 - REC CONDITIONS

```{r}

# Control analysis for CR only on the total sample
semmst_merged_data_filtered_H4_REC_conditions = semmst_merged_data_filtered %>% 
  filter(task == "RecognitionRespAll") %>% 
  filter(cope_name %in% c("LureCR", "FoilCR", "TargetHIT"))

# ASSUMPTION CHECKS
## OUTLIER
semmst_merged_data_filtered_H4_REC_conditions %>%
  group_by(cope_name, roi_cluster) %>%
  identify_outliers(estimate) %>% 
  dplyr::select(ID, roi_cluster, cope_name, is.outlier, is.extreme) %>% 
  filter(is.extreme==TRUE)

semmst_merged_data_filtered_H4_REC_conditions_nooutlier = semmst_merged_data_filtered_H4_REC_conditions %>%
  ungroup()

semmst_merged_H4_REC_conditions_AOV = semmst_merged_data_filtered_H4_REC_conditions_nooutlier %>% 
  droplevels() %>%
  anova_test(dv = estimate, wid = ID, within = c(cope_name, roi_cluster))#, covariate = c(NonWord_sum_scale))

get_anova_table(semmst_merged_H4_REC_conditions_AOV)

#                 Effect DFn DFd     F     p p<.05   ges
## 1             cope_name   2  58 6.967 0.002     * 0.040
## 2           roi_cluster   1  29 2.018 0.166       0.015
## 3 cope_name:roi_cluster   2  58 0.508 0.604       0.002


# POST-HOC
# pairwise comparisons - stim_type * order
semmst_merged_H4_REC_conditions_PWC = semmst_merged_data_filtered_H4_REC_conditions_nooutlier %>%
  group_by(task) %>% 
  pairwise_t_test(
    estimate ~ cope_name, 
    paired = TRUE,
    detailed = TRUE,
    ) %>% 
  ungroup() %>% 
  adjust_pvalue(method = "bonferroni") %>%
  add_significance() %>%
  ungroup() %>% 
  mutate(label = paste0("p=", signif(p.adj, 3)))
semmst_merged_H4_REC_conditions_PWC

##   roi_cluster               estimate .y.      group1 group2      n1    n2 statistic     p    df conf.low conf.high method alternative p.adj 
##   1 L_HEAD_DGCA23_HEAD_SUB_14   0.138  estimate FoilCR LureCR      30    30      3.43 0.002    29  0.0558     0.221  T-test two.sided   0.012 *  
##   4 R_HEAD_DGCA23_HEAD_SUB_15   0.103  estimate FoilCR LureCR      30    30      3.05 0.005    29  0.0341     0.173  T-test two.sided   0.03  * 

# AGAINTS ZERO BASLEINE

semmst_merged_H4_REC_FoilLure_vs0 <- semmst_merged_data_filtered_H4_REC_conditions_nooutlier %>%
  filter(cope_name %in% c("FoilCR", "LureCR")) %>%
  group_by(cope_name) %>%
  t_test(
    estimate ~ 1,
    mu = 0,
    detailed = TRUE
  ) %>%
  adjust_pvalue(method = "bonferroni") %>%
  add_significance("p.adj") %>%
  mutate(label = paste0("p=", signif(p.adj, 3))) %>%
  ungroup()

semmst_merged_H4_REC_FoilLure_vs0

### cope_name estimate .y.      group1 group2         n statistic       p    df conf.low conf.high method alternative  p.adj p.adj.signif label   
## 1 FoilCR      0.0298 estimate 1      null model    60     0.976 0.333      59  -0.0313    0.0909 T-test two.sided   0.666  ns           p=0.666 
## 2 LureCR     -0.0911 estimate 1      null model    60    -2.77  0.00758    59  -0.157    -0.0252 T-test two.sided   0.0152 *            p=0.0152

```


# Figures
## Figure 1 - Behavioral figures (response, LDI)

### Figure 1A - response ratio

```{r}
knitr::opts_chunk$set(
  fig.width  = 11,            # same as ggsave width
  fig.height = 16,            # same as ggsave height
  dpi        = 300,
  fig.retina = 2,             # crisp in HTML
  out.width  = "45%",         # display smaller, but proportions/text scale together
  dev        = "ragg_png"
)

dodge <- 0.7
trial_order <- c("TARGET", "CLOSE", "DISTANT", "FOIL")

# 1) Build per-ID percentages so the two responses sum to 100% within each ID × trial_type
figA_base <- semmst_behav_data_rec_filtered %>%
  filter(!is.na(ID), !is.na(trial_type), !is.na(response)) %>%
  mutate(
    trial_type = factor(trial_type, levels = trial_order),
    response   = factor(response)
  )

resp_lvls <- levels(figA_base$response)

figA_pct <- figA_base %>%
  dplyr::count(ID, trial_type, response, name = "n") %>%
  tidyr::complete(response = factor(resp_lvls, levels = resp_lvls), fill = list(n = 0)) %>%
  dplyr::mutate(
    percent_response = 100 * n / sum(n),
    .by = c(ID, trial_type)
  )

# 2) Within-subject SE across ID for each (trial_type × response)
figA_barsum <- Rmisc::summarySEwithin(
  data       = figA_pct,
  measurevar = "percent_response",
  withinvars = c("trial_type", "response"),
  idvar      = "ID",
  na.rm      = TRUE
)


# Paul Tol "Light" (pastel, print-friendly): light blue / light orange
fill_vals <- setNames(c("#EE8866", "#77AADD"), levels(figA_barsum$response))

behav_fig_A <- ggplot(figA_barsum, aes(
    x = trial_type, y = percent_response,
    fill = response, group = response
  )) +
  geom_col(position = position_dodge(width = dodge), width = 0.70) +
  geom_errorbar(
    aes(ymin = percent_response - se, ymax = percent_response + se),
    position = position_dodge(width = dodge), width = 0.2, size = 1.4
  ) +
  scale_fill_manual(values = fill_vals) +
  scale_y_continuous(limits = c(0, 100), expand = expansion(mult = c(0.01, 0.06))) +
  scale_x_discrete(
    drop = FALSE,
    labels = c(
      "TARGET"  = "TARGET",
      "CLOSE"   = "CLOSE\nLURE",
      "DISTANT" = "DISTANT\nLURE",
      "FOIL"    = "FOIL"
    )
  ) +
  labs(
    x = "Trial type",
    y = "Response percentages",
    fill = "Response"
  ) +
  theme_classic(base_size = 16) +
  theme(
    legend.position = c(0.15, 0.95),
  )

behav_fig_A

```

```{r}
text_base_export=40
behav_fig_A_export <- behav_fig_A +
  theme_classic(base_size = text_base_export) +
  theme(
    legend.position = c(0.18, 0.95),
    legend.title = element_text(size = text_base_export * 0.95),
    legend.text  = element_text(size = text_base_export * 0.90),
    axis.text.x  = element_text(size = text_base_export * 0.90, margin = margin(t = 2)),
    axis.text.y  = element_text(size = text_base_export * 0.90),
    axis.title   = element_text(size = text_base_export * 1.05)
  )

ggsave(
  "derivatives/figures/Figure1A.png",
  plot   = behav_fig_A_export,
  width  = 18, height = 13, units = "in",
  dpi    = 300, bg = "white", device = "png"
)

```


### Figure 1 D - D-primes

```{r}
# 1) Prep & adjustment (remove linear effects of covariates)
figD_plot_base <- semmst_behav_data_rec_LDI_ANCOVA %>%
  filter(!is.na(ID), !is.na(dprime_type), !is.na(dprime_value)) %>%
  mutate(
    dprime_type = factor(dprime_type),
    sex = factor(sex)
  )

# order as: Close, Distant, Target
figD_contrast_order <- c("close_dprime", "distant_dprime", "rec_dprime")
figD_plot_base <- figD_plot_base %>%
  mutate(dprime_type = fct_relevel(dprime_type, figD_contrast_order))

# covariate-only model for adjustment
figD_mod_cov <- lm(dprime_value ~ sex + age + Vocabulary_scale + Digit_Symbol_scale + NonWord_sum_scale,
              data = figD_plot_base)

figD_plot_base <- figD_plot_base %>%
  mutate(dprime_adj = dprime_value - predict(figD_mod_cov, newdata = figD_plot_base) + mean(dprime_value, na.rm = TRUE))

# 2) Labels & colors
figD_x_lab_map <- c(
  "close_dprime"   = "CLOSE\nLURE",
  "distant_dprime" = "DISTANT\nLURE",
  "rec_dprime"  = "FOIL"
)

# Paul Tol (muted): blue / yellow / red — CVD-safe, good in print & grayscale
figD_fill_vals <- c("close_dprime"="#4477AA", "distant_dprime"="#DDCC77", "rec_dprime"="#117733")

# 3) Plot
behav_fig_D <- ggplot(figD_plot_base, aes(x = dprime_type, y = dprime_adj, fill = dprime_type)) +
  geom_boxplot(width = 0.6, outlier.alpha = 0.4, linewidth = 1.8, color = "black") +
  stat_summary(fun = mean, geom = "point", shape = 21,  size = 2.2, fill = "white", color = "black") +
  scale_x_discrete(labels = figD_x_lab_map, drop = FALSE) +
  scale_fill_manual(values = figD_fill_vals, guide = "none") +
  labs(
    x = "Discriminability contrasts",
    y = "Covariate-adjusted d'\n [p(\"old\"|target) - p(\"old\"|condition)]"
  ) +
  theme_classic(base_size = 14)

behav_fig_D

```

```{r}
behav_fig_D_export <- behav_fig_D +
  theme_classic(base_size = 40) +
  theme(
    axis.title = element_text(size = 42),
    axis.text  = element_text(size = 34)
  ) + labs(x = NULL)

ggsave(
  "derivatives/figures/Figure1D.png",
  plot   = behav_fig_D_export,
  width  = 9, height = 16, units = "in",
  dpi    = 300,
  bg     = "white",
  device = "png"   # base png
)
```


### Figure 1 E - continous GLMEM

```{r}
# In this plot, we predict p|old by cosine similarity
# Base data: binary outcome + keep CLOSE & DISTANT only
semmst_behav_data_rec_filtered_GLMEM_plot <- semmst_behav_data_rec_filtered_GLMEM %>%
  mutate(response = as.integer(response == "old")) %>%
  filter(trial_type %in% c("CLOSE", "DISTANT"))
# If your column is 'trial_type', replace 'trial_type' with 'trial_type' above.

# Build a facetting variable: Overall, DISTANT-only, CLOSE-only
semmst_behav_data_rec_filtered_GLMEM_plot_facet <- bind_rows(
  semmst_behav_data_rec_filtered_GLMEM_plot %>% mutate(panel = "ALL LURE"),
  semmst_behav_data_rec_filtered_GLMEM_plot %>% filter(trial_type == "DISTANT") %>% mutate(panel = "DISTANT LURE"),
  semmst_behav_data_rec_filtered_GLMEM_plot %>% filter(trial_type == "CLOSE")   %>% mutate(panel = "CLOSE LURE")
) %>%
  mutate(panel = factor(panel, levels = c("ALL LURE", "DISTANT LURE", "CLOSE LURE")))

# Okabe–Ito (CVD-safe): purple, yellow, blue
figE_cols <- c("ALL LURE" = "#CC79A7", "DISTANT LURE" = "#DDCC77", "CLOSE LURE" = "#4477AA")

behav_fig_E <- ggplot(semmst_behav_data_rec_filtered_GLMEM_plot_facet,
       aes(x = cosine, y = response, color = panel, fill = panel)) +
  geom_smooth(
    method = "glm", method.args = list(family = "binomial"),
    linewidth = 2, se = TRUE, alpha = 0.25
  ) +
  facet_wrap(~ panel, nrow = 1, scales = "free_x") +
  scale_x_continuous(
    breaks = function(lims) round(lims[1] + c(0.1, 0.5, 0.9) * (lims[2] - lims[1]), 2),
    labels = function(x) sprintf("%.2f", x)
  ) +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1)) +
  scale_color_manual(values = figE_cols, guide = "none") +
  scale_fill_manual(values = figE_cols, guide = "none") +
  labs(x = "Cosine similarity", y = "Percentage of 'old' responses") +
  theme_classic(base_size = 14) +
  theme(
    panel.grid.minor = element_blank(),
    strip.text = element_text(face = "bold")
  )

behav_fig_E

```

```{r}

behav_fig_E_export <- behav_fig_E +
  theme_classic(base_size = 40) +
  theme(
    axis.title = element_text(size = 42),
    axis.text  = element_text(size = 32)
  )

ggsave(
  "derivatives/figures/Figure1E.png",
  plot   = behav_fig_E_export,
  width  = 16, height = 16, units = "in",
  dpi    = 300,
  bg     = "white",
  device = "png"   # base png
)

```

### Figure 1 C - Lure cosine similarities

```{r}

figC_plot_base <- semmst_behav_data_rec_filtered %>%
  filter(trial_type %in% c("CLOSE", "DISTANT")) %>%
  mutate(trial_type = factor(trial_type,
                             levels = c("CLOSE", "DISTANT"),
                             labels = c("CLOSE LURE", "DISTANT LURE"))) %>%
  dplyr::select(trial_type, noun, cosine) %>% 
  unique()

# Paul Tol (muted): blue / yellow / red — CVD-safe, good in print & grayscale
figC_fill_vals <- c("CLOSE LURE"="#4477AA", "DISTANT LURE"="#DDCC77")

# 3) Plot
behav_fig_C_hists <- ggplot(figC_plot_base, aes(x = cosine, fill = trial_type)) +
  geom_histogram(
    bins = 20,              # tweak bins/binwidth as you like
    color = "black",
    linewidth = 1.0
  ) +
  facet_wrap(~ trial_type, ncol = 1) +   # <-- vertically stacked (2 panels if 2 trial types)
  scale_fill_manual(values = figC_fill_vals, guide = "none") +
  labs(
    x = "Cosine similarity [1.0 = identical]",
    y = "Number of items in 20 equally spaced bins"
  ) +
  theme_classic(base_size = 14) +
  theme(
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.spacing = unit(0.7, "lines")
  )

behav_fig_C_hists

```


```{r}
behav_fig_C_export <- behav_fig_C_hists +
  theme_classic(base_size = 40) +
  theme(
    axis.title = element_text(size = 38),
    axis.text  = element_text(size = 34)
  ) 

ggsave(
  "derivatives/figures/Figure1C.png",
  plot   = behav_fig_C_export,
  width  = 12, height = 19, units = "in",
  dpi    = 300,
  bg     = "white",
  device = "png"   # base png
)
```


## Figure 2 - ENC RS specificity

```{r}

# BARPLOT
fig2_dodge <- 0.8

fig2_barsum <- Rmisc::summarySEwithin(
  data        = semmst_merged_data_H1_nooutlier,
  measurevar  = "estimate",
  withinvars  = c("stim_type","order", "roi_cluster"),
  idvar       = "ID",
  na.rm       = TRUE
) %>%
  mutate(stim_type = factor(as.character(stim_type),
                            levels = c("Exact","Lure"),
                            labels = c("Exact","Modified")))

fig2_roi_lab <- semmst_merged_data_H1_nooutlier %>%
  dplyr::distinct(roi_cluster, hemisphere, roi, cluster, voxels) %>%
  dplyr::mutate(
    roi_label = dplyr::case_when(
      roi == "HEAD_DGCA23_HEAD_SUB" & hemisphere == "R" ~ "Right DG-CA2/3-SUB cluster",
      roi == "HEAD_DGCA23_HEAD_SUB" & hemisphere == "L" ~ "Left DG-CA2/3-SUB cluster"
    )
  ) %>%
  dplyr::select(roi_cluster, roi_label)

# ------------------------------------------------------------
# NEW: paired tests of stim_type (Exact vs Modified) WITHIN each order,
# collapsed across roi_cluster (same p-values in both facets)
# ------------------------------------------------------------
fig2_stat.test <- semmst_merged_data_H1_nooutlier %>%
  mutate(stim_type = factor(as.character(stim_type),
                            levels = c("Exact","Lure"),
                            labels = c("Exact","Modified"))) %>%
  group_by(ID, order, stim_type) %>%
  summarise(estimate = mean(estimate, na.rm = TRUE), .groups = "drop") %>%
  group_by(order) %>%
  rstatix::t_test(estimate ~ stim_type, paired = TRUE) %>%
  ungroup() %>%
  rstatix::adjust_pvalue(method = "bonferroni") %>%
  rstatix::add_significance("p.adj") %>%
  mutate(
    label = dplyr::case_when(
      p.adj < 0.001 ~ "p < .001",
      p.adj < .01   ~ "p < .01",
      TRUE          ~ paste0("p = ", sub("^0", "", sprintf("%.2f", p.adj)))
    )
  )

# 1) Attach ROI labels to barsum
fig2_barsum <- fig2_barsum %>% dplyr::left_join(fig2_roi_lab, by = "roi_cluster")

# 2) replicate the same stats into both facets and set y.position per facet+order
fig2_stat.test <- fig2_stat.test %>%
  tidyr::crossing(fig2_barsum %>% dplyr::distinct(roi_label)) %>%
  dplyr::left_join(
    fig2_barsum %>%
      dplyr::group_by(order, roi_label) %>%
      dplyr::summarise(y.position = max(estimate + se, na.rm = TRUE) * 1.08, .groups = "drop"),
    by = c("order", "roi_label")
  )

# 3) compute xmin/xmax to connect Exact ↔ Modified within each ORDER (dodge offset)
fig2_stim_lvls <- levels(factor(fig2_barsum$stim_type))  # should be c("Exact","Modified")
exact_idx <- which(fig2_stim_lvls == "Exact")
mod_idx   <- which(fig2_stim_lvls == "Modified")

fig2_stat.test <- fig2_stat.test %>%
  mutate(
    order = factor(order, levels = c("First", "Repeat")),
    offset = if_else(order == "First", -fig2_dodge/2, +fig2_dodge/2),
    xmin = exact_idx + offset,
    xmax = mod_idx   + offset
  )

# --- bar plot (fill by stim_type color, opacity by order), same dodging ---
fig2_plot <- ggplot(fig2_barsum, aes(
    x = stim_type, y = estimate,
    fill = stim_type,           # color by stim type
    group = `order`             # ensures side-by-side bars per stim_type
  )) +
  geom_col(aes(alpha = order), position = position_dodge(width = fig2_dodge), width = 0.65) +
  geom_errorbar(
    aes(ymin = estimate - se, ymax = estimate + se),
    position = position_dodge(width = fig2_dodge), width = 0.15, size=1.2
  ) +
  facet_wrap(~ roi_label) +
  theme_classic(base_size = 13) +
  labs(x = "Condition during encoding", y = "Mean % signal change", fill = "Stimulus", alpha = "Order") +
  # accessible, pleasant green & violet
  scale_fill_manual(values = c(
    "Exact" = "#66BB6A",       # soft green
    "Modified"  = "#9575CD"    # soft violet
  )) +
  # subtle opacity difference for First vs Repeat
  scale_alpha_manual(values = c(
    "First"  = 0.95,
    "Repeat" = 0.55
  )) +
  scale_y_continuous(expand = expansion(mult = c(0.02, 0.14))) +
  custom_theme + guides(fill = "none") +
  theme(
    legend.position = c(0.88, 0.93)  # a bit up
  )

# --- add bracket + p (Exact vs Modified within each order; same in both facets) ---
fig2_plot  +
  ggpubr::stat_pvalue_manual(
    fig2_stat.test,
    label = "label",
    xmin = "xmin",
    xmax = "xmax",
    y.position = "y.position",
    tip.length = 0.01,
    hide.ns = TRUE,
    inherit.aes = FALSE,
    bracket.shorten=1.2,
    size = 5.4,
    bracket.size = 1.0
  )

```

```{r}

text_base_export=40
p_text_size_mm <- text_base_export * 0.20   # ~points → mm-ish (tweak 0.30–0.45)
p_bracket_mm   <- p_text_size_mm * 0.15     # bracket thickness relative to text

fig2_plot_export <- fig2_plot +
  theme_classic(base_size = text_base_export) +
  theme(
    legend.position = c(0.88, 0.88),
    legend.title = element_text(size = text_base_export * 0.88),
    legend.text  = element_text(size = text_base_export * 0.90),
    axis.text.x  = element_text(size = text_base_export * 0.90, margin = margin(t = 2)),
    axis.text.y  = element_text(size = text_base_export * 0.90),
    axis.title   = element_text(size = text_base_export * 1.05),
    strip.text = element_blank(),
    panel.spacing.x = unit(4, "in")
  )

ggsave(
  "derivatives/figures/Figure2B.png",
  plot   = fig2_plot_export,
  width  = 26, height = 13, units = "in",
  dpi    = 300, bg = "white", device = "png"
)

```


## Figure 3 - Power curves

#### Table 1

```{r}

# read MATLAB output(model specs)
fit_long <- read_csv("derivatives/matlab_fit_table_long.csv", show_col_types = FALSE)

# Clean ROI label (same spirit as your facet labels)
make_roi_label <- function(roi_string) {
  parts <- str_split(roi_string, "_", simplify = FALSE)[[1]]
  hemi  <- if (length(parts) >= 1 && parts[1] == "L") "Left " else "Right "

  core <- parts
  if (length(core) >= 2) core <- core[-1]
  if (length(core) >= 1) core <- core[-length(core)]
  core <- core[core != "HEAD"]
  core <- core[core != ""]
  core <- str_replace_all(core, "CA23", "CA2/3")

  paste0(hemi, paste(core, collapse = "-"))
}

# Excel-friendly model string (keep f(x), keep x; we italicize via Excel style)
to_excel_model <- function(s) {
  s %>%
    str_replace_all("\\+\\s*-", " - ") %>%
    str_replace("f\\(x\\)=", "f(x) = ") %>%
    str_replace_all("\\*", "×") %>%
    str_squish()
}

# Build single long table (with ROI only on first row per ROI)
table1_df <- fit_long %>%
  mutate(
    FitType2  = recode(FitType, Power2 = "Power", Linear = "Linear"),
    Winner2   = recode(Winner,  Power2 = "Power", Linear = "Linear"),
    is_winner = (FitType2 == Winner2),
    FitType2  = factor(FitType2, levels = c("Power", "Linear")),
    ROI_lab   = map_chr(ROI, make_roi_label)
  ) %>%
  arrange(ROI, FitType2) %>%
  group_by(ROI) %>%
  mutate(ROI_print = if_else(row_number() == 1, first(ROI_lab), "")) %>%
  ungroup() %>%
  transmute(
    ROI          = ROI_print,
    `Fit type`   = as.character(FitType2),
    Model        = to_excel_model(Model),
    `Adj. R²`    = sprintf("%.3f", AdjR2),
    `R²`         = sprintf("%.3f", R2),
    RMSE         = sprintf("%.3f", RMSE),
    SSE          = sprintf("%.3f", SSE),
    DFE          = as.integer(DFE),
    is_winner
  )

winner_rows <- which(table1_df$is_winner) + 1  # +1 for header row
table1_out  <- table1_df %>% select(-is_winner)

# Write APA Excel
out_file <- "derivatives/figures/Table1.xlsx"
dir.create(dirname(out_file), recursive = TRUE, showWarnings = FALSE)

wb <- createWorkbook()
addWorksheet(wb, "Table1")
showGridLines(wb, "Table1", showGridLines = FALSE)

writeData(wb, "Table1", table1_out, startRow = 1, startCol = 1, colNames = TRUE)

n_data <- nrow(table1_out)
n_col  <- ncol(table1_out)
last_row <- 1 + n_data

#styles
base_style <- createStyle(
  fontName = "Times New Roman", fontSize = 12,
  halign = "left", valign = "center", wrapText = TRUE
)

header_style <- createStyle(
  fontName = "Times New Roman", fontSize = 12,
  textDecoration = "bold",
  halign = "left", valign = "center",
  border = c("top", "bottom"),
  borderStyle = c("thick", "medium"),
  borderColour = c("black", "black")
)

bottom_rule_style <- createStyle(
  border = "bottom", borderStyle = "thick", borderColour = "black"
)

winner_style <- createStyle(textDecoration = "bold")
model_italic <- createStyle(textDecoration = "italic")

foot_style <- createStyle(
  fontName = "Times New Roman", fontSize = 11,
  halign = "left", valign = "top", wrapText = TRUE
)

# ---- apply base style
addStyle(wb, "Table1", base_style,
         rows = 1:last_row, cols = 1:n_col,
         gridExpand = TRUE, stack = TRUE)

# ---- header rules
addStyle(wb, "Table1", header_style,
         rows = 1, cols = 1:n_col,
         gridExpand = TRUE, stack = TRUE)

# ---- bottom rule
addStyle(wb, "Table1", bottom_rule_style,
         rows = last_row, cols = 1:n_col,
         gridExpand = TRUE, stack = TRUE)

# ---- bold winner rows
if (length(winner_rows) > 0) {
  addStyle(wb, "Table1", winner_style,
           rows = winner_rows, cols = 1:n_col,
           gridExpand = TRUE, stack = TRUE)
}

# ---- italicize MODEL column (keeps f(x) and x italic)
model_col <- which(names(table1_out) == "Model")
addStyle(wb, "Table1", model_italic,
         rows = 2:last_row, cols = model_col,
         gridExpand = TRUE, stack = TRUE)

# ---- widths + row heights
setColWidths(wb, "Table1", cols = 1, widths = 22)                 # ROI
setColWidths(wb, "Table1", cols = 2, widths = 10)                 # Fit type
setColWidths(wb, "Table1", cols = 3, widths = 55)                 # Model
setColWidths(wb, "Table1", cols = 4:7, widths = 12)               # numeric cols
setColWidths(wb, "Table1", cols = 8, widths = 8)                  # DFE

setRowHeights(wb, "Table1", rows = 2:last_row, heights = 24)

# ---- footnote (under table)
foot_txt <- paste0(
  "Linear, linear fit; Power, power fit; RMSE, root mean squared error; ",
  "SSE, sum of squares error; DFE, degrees of freedom error"
)

foot_row <- last_row + 2
writeData(wb, "Table1", foot_txt, startRow = foot_row, startCol = 1, colNames = FALSE)
mergeCells(wb, "Table1", cols = 1:n_col, rows = foot_row)
addStyle(wb, "Table1", foot_style, rows = foot_row, cols = 1, stack = TRUE)
setRowHeights(wb, "Table1", rows = foot_row, heights = 35)

saveWorkbook(wb, out_file, overwrite = TRUE)
out_file

```

### Figure 3

From "scripts/smst_mr1_pwoerfunction.m" output

```{r}
# read ROI means
roi_means <- read_csv("derivatives/matlab_roi_means.csv", show_col_types = FALSE)

roi_order <- unique(roi_means$ROI)

roi_means <- roi_means %>%
  mutate(ROI = factor(ROI, levels = roi_order))

#read curves + winner styling + ROI factor IN ONE PIPE
curves <- read_csv("derivatives/matlab_curve_predictions.csv", show_col_types = FALSE) %>%
  mutate(
    is_winner = is_winner == 1,
    linetype  = if_else(is_winner, "solid", "dashed"),
    line_col  = if_else(is_winner, "winner", "other"),
    ROI       = factor(ROI, levels = roi_order)
  )

# read fit table
fit_long <- read_csv("derivatives/matlab_fit_table_long.csv", show_col_types = FALSE)

# facet labels (Fig4-style)
make_roi_label <- function(roi_string) {
  parts <- str_split(roi_string, "_", simplify = TRUE)
  hemi_lab <- if_else(parts[1] == "L", "Left", "Right")

  core <- parts[1, -1]
  core <- core[-length(core)]
  core <- core[core != "HEAD"]

  roi_clean <- paste(core, collapse = "-") %>%
    gsub("HEAD_", "", .) %>%
    gsub("_", "-", .) %>%
    gsub("DG", "DG-", .) %>%
    gsub("2", "2/", .)

  paste(hemi_lab, roi_clean)
}

roi_labeller <- setNames(map_chr(roi_order, make_roi_label), roi_order)

# superscript formatting for ^
to_html_sup <- function(s) {
  s %>%
    str_replace_all("\\^\\s*\\(([^)]+)\\)", "<sup>\\1</sup>") %>%
    str_replace_all("\\^\\s*([A-Za-z0-9\\.]+)", "<sup>\\1</sup>")
}

# annotation per facet: formula + Adj. R² (Power2 row)
figure3_labs <- fit_long %>%
  filter(FitType == "Power2") %>%
  distinct(ROI, .keep_all = TRUE) %>%
  mutate(
    ROI = factor(ROI, levels = roi_order),
    ann = paste0(
      "<i>", to_html_sup(Model), "</i>",
      "<br>Adj. R<sup>2</sup> = ", sprintf("%.3f", AdjR2)
    )
  )

# BASE FIGURE 
fig3 <- ggplot() +
  scale_color_manual(values = c(winner = "red", other = "grey35"), guide = "none") +
  scale_linetype_identity() +
  scale_x_continuous(breaks = 1:3, labels = c("Exact", "Close", "Distant")) +
  facet_wrap(
    ~ ROI,
    scales = "free_y",
    ncol = 2,
    labeller = labeller(ROI = as_labeller(roi_labeller))
  ) +
  coord_cartesian(clip = "off") +
  labs(
    x = "Conditions of repeats during encoding",
    y = "Mean % signal change<br>(corrected for first presentation baseline)"
  ) +
  theme_classic(base_size = 18) +
  custom_theme +
  theme(
    axis.title.y     = ggtext::element_markdown(hjust = 0.5)
  )

# VIEWABLE FIGURE
fig3 +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_point(
    data = roi_means,
    aes(x = x, y = mean_delta),
    size = 2.6
  ) +
  geom_errorbar(
    data = roi_means,
    aes(x = x, ymin = mean_delta - sem_delta, ymax = mean_delta + sem_delta),
    width = 0.05
  ) +
  geom_line(
    data = curves,
    aes(
      x = x, y = y,
      group = interaction(ROI, model),
      color = line_col,
      linetype = linetype
    ),
    linewidth = 1.1
  ) +
  ggtext::geom_richtext(
    data = figure3_labs,
    aes(x = -Inf, y = Inf, label = ann),
    inherit.aes = FALSE,
    hjust = -0.05,
    vjust = 1.7,          
    size = 4.2,
    fill = NA, label.color = NA
  )
```


```{r}
# EXPORT 
text_base_export <- 40

fig3_revised <- fig3 +
  geom_hline(yintercept = 0, linetype = "dotted", linewidth = 1.2) +
  geom_point(
    data = roi_means,
    aes(x = x, y = mean_delta),
    size = 6.0
  ) +
  geom_errorbar(
    data = roi_means,
    aes(x = x, ymin = mean_delta - sem_delta, ymax = mean_delta + sem_delta),
    width = 0.05,
    linewidth = 1.2
  ) +
  geom_line(
    data = curves,
    aes(
      x = x, y = y,
      group = interaction(ROI, model),
      color = line_col,
      linetype = linetype
    ),
    linewidth = 3.2
  ) +
  ggtext::geom_richtext(
    data = figure3_labs,
    aes(x = -Inf, y = Inf, label = ann),
    inherit.aes = FALSE,
    hjust = -0.05,
    vjust = 1.7,       
    size = 10.5,
    fill = NA, label.color = NA
  ) +
  theme_classic(base_size = text_base_export) +
  theme(
    axis.title   = element_text(size = text_base_export * 1.05),
    axis.text.x  = element_text(size = text_base_export * 0.82, margin = margin(t = 2)),
    axis.text.y  = element_text(size = text_base_export * 0.90),
    axis.title.y  = ggtext::element_markdown(hjust = 0.5),
    strip.background = element_rect(fill = "white", color = "black", linewidth = 1.40),
    strip.text = element_text(size = text_base_export * 0.86)
  )


ggsave(
  "derivatives/figures/Figure3.png",
  plot   = fig3_revised,
  width  = 22, height = 12.5, units = "in",
  dpi    = 300, bg = "white", device = "png"
)

```


## Figure 4 - RS ~ LDI

```{r}
# 1) Long table (ALL trials only)
figure4_df <- df_corr_input_all_nooutlier %>%
  dplyr::select(ID, roi_group, roi, hemisphere, bias = LureBiasScore, lure_dprime) %>%
  tidyr::drop_na(bias, lure_dprime) %>%
  dplyr::mutate(
    hemi_lab = dplyr::recode(hemisphere, L = "Left", R = "Right"),
    roi_clean = roi %>%
      gsub("HEAD_", "", .) %>%          # strip HEAD_
      gsub("_", "-", .) %>%
      gsub("DG", "DG-", .) %>%
      gsub("2", "2/", .),
    facet_lab = paste(hemi_lab, roi_clean)
  )

# 2) Per-ROI correlation + Bonferroni + label text
figure4_labs <- figure4_df %>%
  dplyr::group_by(roi_group, facet_lab) %>%
  dplyr::summarise(
    n = dplyr::n(),
    r = unname(stats::cor(bias, lure_dprime, method = "pearson")),
    p = stats::cor.test(bias, lure_dprime, method = "pearson")$p.value,
    .groups = "drop"
  ) %>%
  dplyr::mutate(
    p_adj = p.adjust(p, method = "bonferroni"),
    stars = dplyr::case_when(
      p_adj < .001 ~ "***",
      p_adj < .01  ~ "**",
      p_adj < .05  ~ "*",
      TRUE         ~ ""
    ),
    sig = if_else(p_adj < .05, "sig", "ns"),
    ann = dplyr::case_when(
      is.na(p_adj) ~ sprintf("r = %.2f, p = NA", r),
      p_adj < .001 ~ sprintf("r = %.2f, p < .001%s", r, stars),
      TRUE         ~ sprintf("r = %.2f, p = %.3f%s", r, p_adj, stars)
    )
  )

figure4_full <- figure4_df %>%
  left_join(figure4_labs %>% select(roi_group, sig), by = "roi_group")

# 3) Plot
fig4 = ggplot(figure4_full, aes(bias, lure_dprime)) +
  geom_point(alpha = 0.7, size = 4.5) +
  scale_color_manual(values = c(ns = "grey30", sig = "red"), guide = "none") +
  facet_wrap(~ roi_group, scales = "free",
             labeller = labeller(roi_group = setNames(figure4_labs$facet_lab, figure4_labs$roi_group))) +
  labs(
    x = "Neural pattern separation\nModified repeat - exact repeat\n(% signal change)",
    y = "Behavioral mnemonic discrimination\nd' (lures vs targets)"
  ) +
  theme_classic(base_size = 18) +
  custom_theme

fig4 +
  geom_smooth(aes(color = sig), method = "lm", se = FALSE, linewidth = 1.1) +
  geom_text(
    data = figure4_labs,
    aes(x = -Inf, y = Inf, label = ann, color = sig),
    inherit.aes = FALSE,
    hjust = -0.05, vjust = 1.2, size = 5.5
  )

```

```{r}

text_base_export=40
fig4_export <- fig4 +
  geom_smooth(aes(color = sig), method = "lm", se = FALSE, linewidth = 2.6) +
  geom_text(
    data = figure4_labs,
    aes(x = -Inf, y = Inf, label = ann, color = sig),
    inherit.aes = FALSE,
    hjust = -0.05, vjust = 1.2, size = 10.5
  ) +
  theme_classic(base_size = text_base_export) +
  theme(
    legend.title = element_text(size = text_base_export * 0.95),
    legend.text  = element_text(size = text_base_export * 0.90),
    axis.text.x  = element_text(size = text_base_export * 0.90, margin = margin(t = 2)),
    axis.text.y  = element_text(size = text_base_export * 0.90),
    axis.title   = element_text(size = text_base_export * 1.05)
  )

ggsave(
  "derivatives/figures/Figure4.png",
  plot   = fig4_export,
  width  = 20, height = 12, units = "in",
  dpi    = 300, bg = "white", device = "png"
)

```

## Figure 5 - ENC RS mask -> REC conditions

```{r}

fig5_dodge <- 0.8

level_map <- c("FoilCR", "LureCR", "TargetHIT")
level_lab <- c("Foil",   "Lure",   "Target")

# 1) Within-subject summary
fig5_barsum <- Rmisc::summarySEwithin(
  data        = semmst_merged_data_filtered_H4_REC_conditions_nooutlier,
  measurevar  = "estimate",
  withinvars  = c("cope_name", "roi_cluster"),
  idvar       = "ID",
  na.rm       = TRUE
)

fig5_roi_lab <- semmst_merged_data_filtered_H4_REC_conditions_nooutlier %>%
  distinct(roi_cluster, hemisphere, roi, cluster, voxels) %>%
  mutate(
    roi_label = case_when(
      roi == "HEAD_DGCA23_HEAD_SUB" & hemisphere == "R" ~ "Right DG-CA2/3-SUB",
      roi == "HEAD_DGCA23_HEAD_SUB" & hemisphere == "L" ~ "Left DG-CA2/3-SUB",
      TRUE ~ NA_character_
    )
  ) %>%
  select(roi_cluster, roi_label)

fig5_barsum <- fig5_barsum %>%
  mutate(cope_name = factor(cope_name, levels = level_map, labels = level_lab)) %>%
  left_join(fig5_roi_lab, by = "roi_cluster")

# 2) Base plot (no stats)
fig5_plot <- ggplot(fig5_barsum, aes(x = cope_name, y = estimate, fill = cope_name)) +
  geom_col(position = position_dodge(width = fig5_dodge), width = 0.65) +
  geom_errorbar(
    aes(ymin = estimate - se, ymax = estimate + se),
    position = position_dodge(width = fig5_dodge),
    width = 0.15,
    size = 1.2
  ) +
  facet_wrap(~ roi_label) +
  theme_classic(base_size = 13) +
  labs(x = "Condition during recognition", y = "Mean % signal change") +
  scale_fill_manual(values = c(
    "Target" = "#66BB6A",
    "Lure"   = "#9575CD",
    "Foil"   = "#EE8866"
  )) +
  scale_y_continuous(expand = expansion(mult = c(0.02, 0.12))) +
  custom_theme +
  guides(fill = "none")

# 3) Global paired pairwise stats (collapsed across ROI)
fig5_stats_global <- semmst_merged_data_filtered_H4_REC_conditions_nooutlier %>%
  mutate(cope_name = factor(cope_name, levels = level_map, labels = level_lab)) %>%
  group_by(ID, cope_name) %>%
  summarise(estimate = mean(estimate, na.rm = TRUE), .groups = "drop") %>%
  pairwise_t_test(
    estimate ~ cope_name,
    paired = TRUE,
    p.adjust.method = "bonferroni"
  ) %>%
  mutate(
    label = case_when(
      p.adj < 0.001 ~ "p < .001",
      p.adj < 0.01  ~ "p < .01",
      p.adj < 0.05  ~ "p < .05",
      TRUE ~ paste0("p = ", sub("^0", "", sprintf("%.3f", p.adj)))
    )
  )

# Global ymax across BOTH facets (shared bracket height)
ymax_global <- fig5_barsum %>%
  summarise(ymax = max(estimate + se, na.rm = TRUE)) %>%
  pull(ymax)

# Replicate the same stats into each facet; same y.position levels everywhere
fig5_stats_for_facets <- fig5_barsum %>%
  distinct(roi_label) %>%
  tidyr::crossing(fig5_stats_global) %>%
  group_by(roi_label) %>%
  arrange(group1, group2, .by_group = TRUE) %>%
  mutate(
    y.position = ymax_global * 1.08 + (row_number() - 1) * (0.10 * ymax_global)
  ) %>%
  ungroup()

# 4) In-window plot WITH stats
fig5_plot_with_stats_global <- fig5_plot +
  stat_pvalue_manual(
    fig5_stats_for_facets,
    label = "label",
    xmin = "group1",
    xmax = "group2",
    y.position = "y.position",
    tip.length = 0.01,
    hide.ns = TRUE,
    inherit.aes = FALSE,
    bracket.size = 1.0,
    size = 5.0
  ) +
  scale_y_continuous(expand = expansion(mult = c(0.02, 0.18)))

fig5_plot_with_stats_global
```


```{r}
text_base_export <- 40
p_text_export <- text_base_export * 0.28  # bigger p text on export only

fig5_plot_export <- fig5_plot +
  stat_pvalue_manual(
    fig5_stats_for_facets,
    label = "label",
    xmin = "group1",
    xmax = "group2",
    y.position = "y.position",
    tip.length = 0.01,
    hide.ns = TRUE,
    inherit.aes = FALSE,
    bracket.size = 1.3,
    size = p_text_export
  ) +
  scale_y_continuous(expand = expansion(mult = c(0.02, 0.18))) +
  theme_classic(base_size = text_base_export) +
  theme(
    axis.text.x  = element_text(size = text_base_export * 0.90, margin = margin(t = 2)),
    axis.text.y  = element_text(size = text_base_export * 0.90),
    axis.title   = element_text(size = text_base_export * 1.05),
    strip.text   = element_text(size = text_base_export * 0.95)
  )

ggsave(
  "derivatives/figures/Figure5.png",
  plot   = fig5_plot_export,
  width  = 22, height = 14, units = "in",
  dpi    = 300, bg = "white", device = "png"
)

```



# Supplementary Results
### Supplementary Results 1 - covariate effects

#### Behavioural GLMEM covariates

```{r}

model_complex_cont = glmer(response ~ cosine * trial_type * former_type +
                                        age + sex + education + Vocabulary_scale + Digit_Symbol_scale +
                                                  NonWord_sum_scale + arousal_scale + meaningfulness_scale + concreteness_scale +
                                        (1|ID) + 
                                        (1|itemno),
                                        family = binomial("probit"), 
                                        data = semmst_behav_data_rec_filtered_GLMEM_lure,
                                        control = glmerControl(optimizer ='bobyqa', optCtrl=list(maxfun = 20000)), nAGQ=0)

```



##### Supplementary Figure 2AB.

```{r}
# 1) Marginal (averaged-over-covariates) predictions
pred_nonword <- ggeffects::ggaverage(
  model_complex_cont,
  terms = "NonWord_sum_scale [n=100]"   # smooth grid
) %>%
  as.data.frame() %>%
  mutate(effect = "Phonological awareness of participants")

pred_meaning <- ggeffects::ggaverage(
  model_complex_cont,
  terms = "meaningfulness_scale [n=100]"
) %>%
  as.data.frame() %>%
  mutate(effect = "Meaningfulness of items")

preds_2ABSI <- bind_rows(pred_nonword, pred_meaning)

# 2) Plot (2 facets next to each other)
fig_ABSI_behav <- ggplot(preds_2ABSI, aes(x = x, y = predicted)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.18, fill="#4C72B0") +
  geom_line(size = 1.2, colour="#4C72B0") +
  facet_wrap(~ effect, nrow = 1, scales = "free_x") +
  theme_classic(base_size = 13) +
  labs(
    x = NULL,
    y = "p(response 'old'|lure)"
  ) +
  scale_y_continuous(limits = c(0, 0.5), expand = expansion(mult = c(0.02, 0.06))) +
  custom_theme

fig_ABSI_behav
```


```{r}
# 3) Export (matches your Figure2B export approach)
text_base_export <- 40

fig_ABSI_export <- fig_ABSI_behav +
  theme_classic(base_size = text_base_export) +
  theme(
    axis.text.x  = element_text(size = text_base_export * 0.90, margin = margin(t = 2)),
    axis.text.y  = element_text(size = text_base_export * 0.90),
    axis.title   = element_text(size = text_base_export * 1.05)
  )

ggsave(
  "derivatives/figures/SI_figures/Figure2ABSI.png",
  plot   = fig_ABSI_export,
  width  = 21, height = 11, units = "in",
  dpi    = 300, bg = "white", device = "png"
)


```


#### Encoding ANCOVA MEDIAN SPLIT (Digit-Symbol)
```{r}

df <- semmst_merged_data_H1_nooutlier %>% 
  drop_na(Digit_Symbol) %>% 
  mutate(Digit_Symbol_scale = scale(Digit_Symbol))

df_E1 <- df %>%
  mutate(
    digit_group = if_else(Digit_Symbol_scale >= median(Digit_Symbol_scale, na.rm = TRUE), "High", "Low"),
    digit_group = factor(digit_group, levels = c("Low", "High"))
  )

semmst_merged_data_E1_digit_median_split = df_E1 %>%
  group_by(stim_type, digit_group) %>% 
  pairwise_t_test(
    estimate ~ order, 
    paired = TRUE,
    detailed = TRUE,
    ) %>% 
  ungroup() %>% 
  adjust_pvalue(method = "bonferroni") %>%
  add_significance() %>%
  ungroup() %>% 
  mutate(label = paste0("p=", signif(p.adj, 3)))
semmst_merged_data_E1_digit_median_split

#  stim_type digit_group estimate .y.      group1 group2    n1    n2 statistic         p    df conf.low conf.high method alternative   p.adj
## 1 Exact     Low           0.221  estimate First  Repeat    28    28      8.04   1.22e-8    27   0.164      0.277 T-test two.sided   4.88e-8 ****       
## 2 Exact     High          0.158  estimate First  Repeat    28    28      4.92   3.82e-5    27   0.0923     0.225 T-test two.sided   1.53e-4 ***        
## 3 Lure      Low           0.0490 estimate First  Repeat    28    28      1.54   1.36e-1    27  -0.0165     0.115 T-test two.sided   5.44e-1 ns         
## 4 Lure      High          0.0949 estimate First  Repeat    28    28      3.53   2   e-3    27   0.0397     0.150 T-test two.sided   8   e-3 **         

```

##### Supplementary Figure 2C.

```{r}
fig_mediansplit_CSI_dodge <- 0.8

# OPTIONAL but recommended if you have multiple rows per ID/condition (e.g., ROI clusters):
# collapse to one value per ID × stim_type × order × digit_group
df_E1_collapsed <- df_E1 %>%
  group_by(ID, stim_type, order, digit_group) %>%
  mutate(stim_type = factor(as.character(stim_type),
                       levels = c("Exact", "Lure"),
                       labels = c("Exact", "Modified"))) %>% 
  mutate(digit_group = factor(as.character(digit_group),
                       levels = c("Low", "High"),
                       labels = c("Low processing speed", "High processing speed")))

# --- summary for bars (within-subject correction for stim_type+order, between = digit_group) ---
fig_mediansplit_CSI_barsum <- Rmisc::summarySEwithin(
  data       = df_E1_collapsed,
  measurevar = "estimate",
  withinvars = c("stim_type", "order"),
  betweenvars = "digit_group",
  idvar      = "ID",
  na.rm      = TRUE
)

# --- paired tests: First vs Repeat within each stim_type × digit_group ---
fig_mediansplit_CSI_stat.test <- df_E1_collapsed %>%
  group_by(stim_type, digit_group) %>%
  pairwise_t_test(
    estimate ~ order,
    paired = TRUE,
    detailed = TRUE
  ) %>%
  ungroup() %>%
  adjust_pvalue(method = "bonferroni") %>%
  add_significance("p.adj") %>%
  mutate(
    label = case_when(
      p.adj < 0.001 ~ "p < .001",
      p.adj < 0.01  ~ "p < .01",
      p.adj < 0.05  ~ "p < .05",
      TRUE          ~ paste0("p = ", sub("^0", "", sprintf("%.2f", p.adj)))
    )
  )

# y positions per facet + stim_type
fig_mediansplit_CSI_stat.test <- fig_mediansplit_CSI_stat.test %>%
  left_join(
    fig_mediansplit_CSI_barsum %>%
      group_by(stim_type, digit_group) %>%
      summarise(y.position = max(estimate + se, na.rm = TRUE) * 1.08, .groups = "drop"),
    by = c("stim_type", "digit_group")
  ) %>%
  mutate(
    stim_idx = as.numeric(stim_type),
    xmin = stim_idx - fig_mediansplit_CSI_dodge/2,
    xmax = stim_idx + fig_mediansplit_CSI_dodge/2
  )

# --- plot ---
fig_mediansplit_CSI_plot <- ggplot(
  fig_mediansplit_CSI_barsum,
  aes(x = stim_type, y = estimate, fill = stim_type, group = order)
) +
  geom_col(
    aes(alpha = order),
    position = position_dodge(width = fig_mediansplit_CSI_dodge),
    width = 0.65
  ) +
  geom_errorbar(
    aes(ymin = estimate - se, ymax = estimate + se),
    position = position_dodge(width = fig_mediansplit_CSI_dodge),
    width = 0.15, size = 1.2
  ) +
  facet_wrap(~ digit_group) +
  theme_classic(base_size = 13) +
  labs(
    x = "Condition during encoding",
    y = "Mean % signal change",
    fill = "Stimulus",
    alpha = "Order"
  ) +
  scale_fill_manual(values = c(
    "Exact"     = "#66BB6A",
    "Modified"  = "#9575CD"
  )) +
  scale_alpha_manual(values = c(
    "First"  = 0.95,
    "Repeat" = 0.55
  )) +
  scale_y_continuous(expand = expansion(mult = c(0.02, 0.14))) +
  custom_theme +
  guides(fill = "none") +
  theme(
    legend.position = c(0.88, 0.13)
  )

fig_mediansplit_CSI_plot +
  ggpubr::stat_pvalue_manual(
    fig_mediansplit_CSI_stat.test,
    label = "label",
    xmin = "xmin",
    xmax = "xmax",
    y.position = "y.position",
    tip.length = 0.01,
    hide.ns = TRUE,
    inherit.aes = FALSE,
    bracket.shorten = 1.2,
    size = 5.4,
    bracket.size = 1.0
  )
```


```{r}
text_base_export <- 40

fig_mediansplit_CSI_plot_export <- fig_mediansplit_CSI_plot +
  ggpubr::stat_pvalue_manual(
    fig_mediansplit_CSI_stat.test,
    label = "label",
    xmin = "xmin",
    xmax = "xmax",
    y.position = "y.position",
    tip.length = 0.01,
    hide.ns = TRUE,
    inherit.aes = FALSE,
    bracket.shorten = 1.2,
    size = 8.4,
    bracket.size = 1.4
  ) +
  theme_classic(base_size = text_base_export) +
  theme(
    legend.position = c(0.88, 0.12),
    legend.title = element_text(size = text_base_export * 0.88),
    legend.text  = element_text(size = text_base_export * 0.90),
    axis.text.x  = element_text(size = text_base_export * 0.90, margin = margin(t = 2)),
    axis.text.y  = element_text(size = text_base_export * 0.90),
    axis.title   = element_text(size = text_base_export * 1.05)
  )

ggsave(
  "derivatives/figures/SI_figures/Figure2CSI.png",
  plot   = fig_mediansplit_CSI_plot_export,
  width  = 21, height = 13, units = "in",
  dpi    = 300, bg = "white", device = "png"
)

```


### Supplementary Results 2 - Anatomical power vs linear funcs

```{r}
# FILTER DATA
semmst_merged_data_H1_clodis_powerfunc_anat = semmst_merged_data_filtered_anat %>% 
  filter(task == "EncodingFirst") %>% 
  filter(cope_name %in% c("AllFirst", "CloseRepeat", "DistantRepeat", "ExactRepeat")) %>% 
  mutate(roi_cluster = paste(hemisphere, roi, sep = "_")) %>% 
  mutate(cope_name = factor(cope_name, levels = c("ExactRepeat", "CloseRepeat", "DistantRepeat", "AllFirst"))) %>% 
  mutate(roi_cluster = factor(roi_cluster))

# OUTLIER
semmst_merged_data_H1_clodis_powerfunc_anat %>%
  group_by(cope_name, roi_cluster) %>%
  identify_outliers(estimate) %>% 
  dplyr::select(ID, is.outlier, is.extreme) %>% 
  filter(is.extreme == TRUE)

semmst_merged_data_H1_clodis_powerfunc_anat_nooutlier = semmst_merged_data_H1_clodis_powerfunc_anat 

## EXPORT TO MATLAB
export_matlab_anat <- semmst_merged_data_H1_clodis_powerfunc_anat_nooutlier %>%
  filter(cope_name %in% c("AllFirst","ExactRepeat","CloseRepeat","DistantRepeat")) %>%
  transmute(
    Subj = ID,
    ROI  = as.character(roi_cluster),
    Cond = as.character(cope_name),
    Beta = estimate
  )

write.csv(export_matlab_anat, "derivatives/transfer_raw_matlab_anat.csv", row.names = FALSE)

```

The rest of this analysis is in "scripts/smst_mr1_powerfunction_anat.m"

#### Supplementary Figure 3

Import outputs from "scripts/smst_mr1_powerfunction_anat.m"

```{r}
## HELPERS
to_html_sup <- function(s) {
  s %>%
    str_replace_all("\\^\\s*\\(([^)]+)\\)", "<sup>\\1</sup>") %>%
    str_replace_all("\\^\\s*([A-Za-z0-9\\.]+)", "<sup>\\1</sup>")
}

parse_roi_clean <- function(roi_string) {
  parts <- str_split(roi_string, "_")[[1]]
  core  <- parts[-1]               # drop L/R
  core  <- core[-length(core)]     # drop last token
  core  <- core[core != "HEAD"]    # remove HEAD token

  paste(core, collapse = "-") %>%
    gsub("HEAD", "", .) %>%
    gsub("_", "-", .) %>%
    gsub("DG", "DG-", .) %>%
    gsub("CA2", "CA2/", .) %>% 
    gsub("CA12", "CA1/2", .)
}

# Read-in + format
roi_means_anat <- read_csv("derivatives/matlab_roi_means_anat.csv", show_col_types = FALSE) %>%
  mutate(
    hemi_lab  = if_else(str_starts(ROI, "L"), "Left hemisphere", "Right hemisphere"),
    roi_type  = if_else(str_detect(ROI, "HEAD"), "head", "body"),
    roi_clean = map_chr(ROI, parse_roi_clean)
  )

roi_clean_order <- unique(roi_means_anat$roi_clean)

roi_means_anat <- roi_means_anat %>%
  mutate(
    roi_type  = factor(roi_type, levels = c("head", "body")),
    hemi_lab  = factor(hemi_lab, levels = c("Left hemisphere", "Right hemisphere")),
    roi_clean = factor(roi_clean, levels = roi_clean_order)
  )

curves_anat <- read_csv("derivatives/matlab_curve_predictions_anat.csv", show_col_types = FALSE) %>%
  mutate(
    is_winner = is_winner == 1,
    linetype  = if_else(is_winner, "solid", "dashed"),
    line_col  = if_else(is_winner, "winner", "other"),
    hemi_lab  = if_else(str_starts(ROI, "L"), "Left hemisphere", "Right hemisphere"),
    roi_type  = if_else(str_detect(ROI, "HEAD"), "head", "body"),
    roi_clean = map_chr(ROI, parse_roi_clean)
  ) %>%
  mutate(
    roi_type  = factor(roi_type, levels = c("head", "body")),
    hemi_lab  = factor(hemi_lab, levels = c("Left hemisphere", "Right hemisphere")),
    roi_clean = factor(roi_clean, levels = roi_clean_order)
  )

fit_long_anat <- read_csv("derivatives/matlab_fit_table_long_anat.csv", show_col_types = FALSE)

# WINNER model
labs_anat <- fit_long_anat %>%
  filter(FitType == Winner) %>%                # <-- WINNER ONLY
  distinct(ROI, .keep_all = TRUE) %>%
  mutate(
    hemi_lab  = if_else(str_starts(ROI, "L"), "Left hemisphere", "Right hemisphere"),
    roi_type  = if_else(str_detect(ROI, "HEAD"), "head", "body"),
    roi_clean = map_chr(ROI, parse_roi_clean),
    roi_type  = factor(roi_type, levels = c("head", "body")),
    hemi_lab  = factor(hemi_lab, levels = c("Left hemisphere", "Right hemisphere")),
    roi_clean = factor(roi_clean, levels = roi_clean_order),
    ann = paste0(
      "<i>", to_html_sup(Model), "</i>",
      "<br>Adj. R<sup>2</sup> = ", sprintf("%.3f", AdjR2)
    )
  )


# Panels (HEAD and BODY)
make_anat_panel <- function(which_type, title_txt,
                            base_size = 14, point_size = 2.4,
                            line_lwd = 1.0, ann_size = 4.0) {

  ggplot() +
    geom_hline(yintercept = 0, linetype = "dotted") +
    geom_point(
      data = roi_means_anat %>% filter(roi_type == which_type),
      aes(x = x, y = mean_delta),
      size = point_size
    ) +
    geom_errorbar(
      data = roi_means_anat %>% filter(roi_type == which_type),
      aes(x = x, ymin = mean_delta - sem_delta, ymax = mean_delta + sem_delta),
      width = 0.05
    ) +
    geom_line(
      data = curves_anat %>% filter(roi_type == which_type),
      aes(
        x = x, y = y,
        group = interaction(ROI, model),
        color = line_col,
        linetype = linetype
      ),
      linewidth = line_lwd
    ) +

    # LEFT hemisphere annotation: top-left
    ggtext::geom_richtext(
      data = labs_anat %>% filter(roi_type == which_type, hemi_lab == "Left hemisphere"),
      aes(x = -Inf, y = Inf, label = ann),
      inherit.aes = FALSE,
      hjust = -0.05, vjust = 1.7,
      size = ann_size,
      fill = NA, label.color = NA
    ) +

    # RIGHT hemisphere annotation: bottom-right
    ggtext::geom_richtext(
      data = labs_anat %>% filter(roi_type == which_type, hemi_lab == "Right hemisphere"),
      aes(x = Inf, y = -Inf, label = ann),
      inherit.aes = FALSE,
      hjust = 1.05, vjust = -0.25,
      size = ann_size,
      fill = NA, label.color = NA
    ) +

    scale_color_manual(values = c(winner = "red", other = "grey35"), guide = "none") +
    scale_linetype_identity() +
    scale_x_continuous(breaks = 1:3, labels = c("Exact", "Close", "Distant")) +
    facet_grid(rows = vars(roi_clean), cols = vars(hemi_lab), scales = "free_y") +
    coord_cartesian(clip = "off") +
    labs(
      x = "Conditions of repeats during encoding",
      y = "Mean % signal change<br>(corrected for first presentation baseline)",
      title = title_txt
    ) +
    theme_classic(base_size = base_size) +
    custom_theme +
    theme(
      plot.title = element_text(hjust = 0.5, face = "bold"),
      strip.background = element_blank(),
      strip.text = element_text(face = "bold"),

      # <-- bigger gap between the 2 hemisphere columns:
      panel.spacing.x = unit(1.25, "lines"),
      panel.spacing.y = unit(0.6, "lines"),

      axis.title.y = ggtext::element_markdown(hjust = 0.5)
    )
}

# VIEW
p_head_view <- make_anat_panel("head", "Hippocampal head",
                               base_size = 14, point_size = 2.4, line_lwd = 1.0, ann_size = 4.0)

p_body_view <- make_anat_panel("body", "Hippocampal body",
                               base_size = 14, point_size = 2.4, line_lwd = 1.0, ann_size = 4.0)

supp_fig_anat_curves <- p_head_view | p_body_view
supp_fig_anat_curves

```


```{r}
p_head_export <- make_anat_panel("head", "Hippocampal head",
                                 base_size = 24, point_size = 5.5, line_lwd = 2.6, ann_size = 9.5)

p_body_export <- make_anat_panel("body", "Hippocampal body",
                                 base_size = 24, point_size = 5.5, line_lwd = 2.6, ann_size = 9.5)

supp_fig_anat_curves_export <- p_head_export | p_body_export

ggsave(
  "derivatives/figures/SI_figures/Figure3SI.png",
  plot   = supp_fig_anat_curves_export,
  width  = 32, height = 20.5, units = "in",
  dpi    = 300, bg = "white", device = ragg::agg_png
)

```

#### Supplementary Table 1.

```{r}

# read MATLAB output (anat)
fit_long_anat <- read_csv("derivatives/matlab_fit_table_long_anat.csv", show_col_types = FALSE)

#ROI label (same as earlier)
make_roi_label <- function(roi_string) {
  parts <- str_split(roi_string, "_", simplify = FALSE)[[1]]
  hemi  <- if (length(parts) >= 1 && parts[1] == "L") "Left " else "Right "

  core <- parts
  if (length(core) >= 2) core <- core[-1]
  if (length(core) >= 1) core <- core[-length(core)]
  core <- core[core != "HEAD"]
  core <- core[core != ""]
  core <- str_replace_all(core, "CA23", "CA2/3")

  paste0(hemi, paste(core, collapse = "-"))
}

# Excel strings
to_excel_model <- function(s) {
  s %>%
    str_replace_all("\\+\\s*-", " - ") %>%
    str_replace("f\\(x\\)=", "f(x) = ") %>%
    str_replace_all("\\*", "×") %>%
    str_squish()
}

# Build single long table (ROI only on first row per ROI)
supp_table1_anat <- fit_long_anat %>%
  mutate(
    FitType2  = recode(FitType, Power2 = "Power", Linear = "Linear"),
    Winner2   = recode(Winner,  Power2 = "Power", Linear = "Linear"),
    is_winner = (FitType2 == Winner2),
    FitType2  = factor(FitType2, levels = c("Power", "Linear")),
    ROI_lab   = map_chr(ROI, make_roi_label)
  ) %>%
  arrange(ROI, FitType2) %>%
  group_by(ROI) %>%
  mutate(ROI_print = if_else(row_number() == 1, first(ROI_lab), "")) %>%
  ungroup() %>%
  transmute(
    ROI        = ROI_print,
    `Fit type` = as.character(FitType2),
    Model      = to_excel_model(Model),
    `Adj. R²`  = sprintf("%.3f", AdjR2),
    `R²`       = sprintf("%.3f", R2),
    RMSE       = sprintf("%.3f", RMSE),
    SSE        = sprintf("%.3f", SSE),
    DFE        = as.integer(DFE),
    is_winner
  )

winner_rows <- which(supp_table1_anat$is_winner) + 1  # +1 for header row
supp_table1_out <- supp_table1_anat %>% select(-is_winner)

# Write APA Excel
out_file <- "derivatives/figures/SI_figures/SupplementaryTable1.xlsx"

wb <- createWorkbook()
addWorksheet(wb, "SupplementaryTable1")
showGridLines(wb, "SupplementaryTable1", showGridLines = FALSE)

writeData(wb, "SupplementaryTable1", supp_table1_out, startRow = 1, startCol = 1, colNames = TRUE)

n_data   <- nrow(supp_table1_out)
n_col    <- ncol(supp_table1_out)
last_row <- 1 + n_data

# ---- styles
base_style <- createStyle(
  fontName = "Times New Roman", fontSize = 12,
  halign = "left", valign = "center", wrapText = TRUE
)

header_style <- createStyle(
  fontName = "Times New Roman", fontSize = 12,
  textDecoration = "bold",
  halign = "left", valign = "center",
  border = c("top", "bottom"),
  borderStyle = c("thick", "medium"),
  borderColour = c("black", "black")
)

bottom_rule_style <- createStyle(
  border = "bottom", borderStyle = "thick", borderColour = "black"
)

winner_style <- createStyle(textDecoration = "bold")
model_italic <- createStyle(textDecoration = "italic")

foot_style <- createStyle(
  fontName = "Times New Roman", fontSize = 11,
  halign = "left", valign = "top", wrapText = TRUE
)

# ---- apply base style
addStyle(wb, "SupplementaryTable1", base_style,
         rows = 1:last_row, cols = 1:n_col,
         gridExpand = TRUE, stack = TRUE)

# ---- header rules
addStyle(wb, "SupplementaryTable1", header_style,
         rows = 1, cols = 1:n_col,
         gridExpand = TRUE, stack = TRUE)

# ---- bottom rule
addStyle(wb, "SupplementaryTable1", bottom_rule_style,
         rows = last_row, cols = 1:n_col,
         gridExpand = TRUE, stack = TRUE)

# ---- bold winner rows
if (length(winner_rows) > 0) {
  addStyle(wb, "SupplementaryTable1", winner_style,
           rows = winner_rows, cols = 1:n_col,
           gridExpand = TRUE, stack = TRUE)
}

# ---- italicize MODEL column
model_col <- which(names(supp_table1_out) == "Model")
addStyle(wb, "SupplementaryTable1", model_italic,
         rows = 2:last_row, cols = model_col,
         gridExpand = TRUE, stack = TRUE)

# ---- column widths + row heights
setColWidths(wb, "SupplementaryTable1", cols = 1, widths = 22)     # ROI
setColWidths(wb, "SupplementaryTable1", cols = 2, widths = 10)     # Fit type
setColWidths(wb, "SupplementaryTable1", cols = 3, widths = 55)     # Model
setColWidths(wb, "SupplementaryTable1", cols = 4:7, widths = 12)   # numeric cols
setColWidths(wb, "SupplementaryTable1", cols = 8, widths = 8)      # DFE

setRowHeights(wb, "SupplementaryTable1", rows = 2:last_row, heights = 24)

# ---- footnote
foot_txt <- paste0(
  "Linear, linear fit; Power, power fit; RMSE, root mean squared error; ",
  "SSE, sum of squares error; DFE, degrees of freedom error"
)

foot_row <- last_row + 2
writeData(wb, "SupplementaryTable1", foot_txt, startRow = foot_row, startCol = 1, colNames = FALSE)
mergeCells(wb, "SupplementaryTable1", cols = 1:n_col, rows = foot_row)
addStyle(wb, "SupplementaryTable1", foot_style, rows = foot_row, cols = 1, stack = TRUE)
setRowHeights(wb, "SupplementaryTable1", rows = foot_row, heights = 35)

saveWorkbook(wb, out_file, overwrite = TRUE)
out_file

```


### Supplementary Results 3 - anatomical masks

```{r}

# FILTER DATA
semmst_merged_data_filtered_anat_H1 = semmst_merged_data_filtered_anat %>% 
  filter(task == "Encoding") %>% 
  filter(cope_name %in% c("LureFirst", "ExactFirst", "LureRepeat", "ExactRepeat")) %>% 
  extract(
    col = cope_name,
    into = c("stim_type", "order"),
    regex = "([A-Za-z]+?)(First|Repeat)$"
  ) %>% 
  mutate(
    stim_type = as.factor(stim_type),
    order = as.factor(order)
  ) %>% 
  mutate(stim_type = factor(stim_type, levels = c("Exact", "Lure"))) %>% 
  mutate(
    stim_type = factor(stim_type, levels = c("Exact", "Lure")),
    order = factor(order),
    roi_type = if_else(str_detect(roi, "HEAD"), "head", "body")
  ) %>% 
  mutate(roi = str_remove(roi, "^HEAD")) %>% 
  mutate(roi = str_replace_all(roi, c("CA12" = "CA1", "DGCA3" = "DGCA23")))
  

# ASSUMPTION CHECKS
## OUTLIER
semmst_merged_data_filtered_anat_H1 %>%
  group_by(stim_type, order, roi_type, roi, hemisphere) %>%
  identify_outliers(estimate) %>% 
  dplyr::select(ID, is.outlier, is.extreme) %>% 
  filter(is.extreme==TRUE)

semmst_merged_data_filtered_anat_H1_nooutlier = semmst_merged_data_filtered_anat_H1 %>%
  group_by(stim_type, order, roi_type, roi, hemisphere) %>%
  filter(! ID %in% c("sub-499854", "sub-982347")) %>%  #, " sub-012421", "sub-632012", "sub-800472")) %>% # c("sub-434971", "sub-982347")) %>%
  ungroup()

##NORMALITY
semmst_merged_data_filtered_anat_H1_nooutlier %>% 
  group_by(stim_type, order, roi_type) %>%
  shapiro_test(estimate)

# ANOVA
semmst_merged_data_filtered_anat_H1_nooutlier_AOV = semmst_merged_data_filtered_anat_H1_nooutlier %>%
  anova_test(dv = estimate, wid = ID, within = c(stim_type, order, roi_type, roi, hemisphere))#, covariate = c(NonWord_sum_scale, Digit_Symbol_scale))

get_anova_table(semmst_merged_data_filtered_anat_H1_nooutlier_AOV)

# REPORT                       Effect DFn DFd      F        p p<.05      ges
## 2                                    order 1.00 27.00  7.018 0.013000     * 1.20e-02
## 3                                 roi_type 1.00 27.00  6.161 0.020000     * 1.20e-02
## 4                                      roi 1.62 43.73  8.448 0.002000     * 2.50e-02
## 8                           order:roi_type 1.00 27.00 19.939 0.000128     * 1.40e-02
## 9                            stim_type:roi 2.00 54.00  4.516 0.015000     * 2.00e-03
## 10                               order:roi 2.00 54.00  4.942 0.011000     * 2.00e-03
## 11                            roi_type:roi 2.00 54.00  4.526 0.015000     * 9.00e-03
## 13                        order:hemisphere 1.00 27.00  8.986 0.006000     * 3.00e-03
## 19                      order:roi_type:roi 2.00 54.00  6.649 0.003000     * 2.00e-03

```

#### Supplementary Figure 4.

```{r}

fig_dodge <- 0.8

# within-subject summary per stim_type × order × roi_type × roi × hemisphere
figSI_anat_encRS_barsum <- Rmisc::summarySEwithin(
  data       = semmst_merged_data_filtered_anat_H1_nooutlier,
  measurevar = "estimate",
  withinvars = c("stim_type","order","roi_type","roi","hemisphere"),
  idvar      = "ID",
  na.rm      = TRUE
) %>%
  mutate(
    stim_type  = factor(stim_type, levels = c("Exact", "Lure")),
    order      = factor(order, levels = c("First", "Repeat")),
    roi_type   = factor(roi_type, levels = c("head", "body")),
    roi        = factor(roi),
    hemisphere = factor(
      hemisphere,
      levels = c("L", "R"),
      labels = c("Left hemisphere", "Right hemisphere")
    )
  )%>%
  mutate(stim_type = factor(as.character(stim_type),
                            levels = c("Exact","Lure"),
                            labels = c("Exact","Modified")))

make_panel <- function(df) {
  ggplot(df, aes(
    x = stim_type, y = estimate,
    fill = stim_type,
    alpha = order,
    group = order
  )) +
    geom_col(position = position_dodge(width = fig_dodge), width = 0.65) +
    geom_errorbar(
      aes(ymin = estimate - se, ymax = estimate + se),
      position = position_dodge(width = fig_dodge),
      width = 0.15,
      linewidth = 1.1
    ) +
    facet_grid(rows = vars(roi), cols = vars(hemisphere)) +
    theme_classic(base_size = 13) +
    labs(x = "Condition during encoding", y = "Mean % signal change", alpha = "Order") +
    scale_fill_manual(values = c("Exact" = "#66BB6A", "Modified" = "#9575CD")) +
    scale_alpha_manual(values = c("First" = 0.95, "Repeat" = 0.55)) +
    scale_y_continuous(expand = expansion(mult = c(0.02, 0.12))) +
    guides(
      fill  = "none",
      alpha = guide_legend(title = "Order")
    ) +
    theme(
      strip.background = element_blank(),
      strip.text = element_text(face = "bold"),
      panel.spacing = unit(0.6, "lines")
    )
}

# Left panel (head): no legend
p_head_figSI_anat_encRS <- figSI_anat_encRS_barsum %>%
  filter(roi_type == "head") %>%
  make_panel() +
  ggtitle("Hippocampal head") +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    legend.position = "none"
  )

# Right panel (body): legend inset top-right
p_body_figSI_anat_encRS <- figSI_anat_encRS_barsum %>%
  filter(roi_type == "body") %>%
  make_panel() +
  ggtitle("Hippocampal body") +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    legend.position      = c(0.98, 0.98),
    legend.justification = c(1, 1),
    legend.background    = element_rect(fill = alpha("white", 0.75), colour = NA),
    legend.key           = element_blank()
  )

# Combine as two columns (IMPORTANT: no guide collection)
figSI_anat_encRS_plot <- (p_head_figSI_anat_encRS | p_body_figSI_anat_encRS)

figSI_anat_encRS_plot

```


```{r}

text_base_export <- 24  # 20–28 usually looks best for this many facets

# IMPORTANT: do NOT set legend.position in the export theme
export_theme <- theme_classic(base_size = text_base_export) +
  theme(
    axis.text.x   = element_text(size = text_base_export * 0.80, margin = margin(t = 6)),
    axis.text.y   = element_text(size = text_base_export * 0.80),
    axis.title.x  = element_text(size = text_base_export * 0.95, margin = margin(t = 10)),
    axis.title.y  = element_text(size = text_base_export * 0.95, margin = margin(r = 10)),
    strip.text    = element_text(size = text_base_export * 0.85, face = "bold"),
    plot.title    = element_text(size = text_base_export * 1.05, face = "bold", hjust = 0.5),
    legend.title  = element_text(size = text_base_export * 0.85),
    legend.text   = element_text(size = text_base_export * 0.80),
    panel.spacing = unit(0.8, "lines")
  )

# Apply export theme per panel + enforce legend behavior
p_head_export <- p_head_figSI_anat_encRS &
  export_theme &
  theme(legend.position = "none")

p_body_export <- p_body_figSI_anat_encRS &
  export_theme &
  theme(
    legend.position      = c(0.98, 0.98),   # inside top-right of RIGHT panel
    legend.justification = c(1, 1),
    legend.background    = element_rect(fill = alpha("white", 0.75), colour = NA),
    legend.key           = element_blank()
  )

figSI_anat_encRS_plot_export <- p_head_export | p_body_export

ggsave(
  "derivatives/figures/SI_figures/Figure4SI.png",
  plot   = figSI_anat_encRS_plot_export,
  width  = 23, height = 12, units = "in",
  dpi    = 300, bg = "white", device = ragg::agg_png
)

```

### Supplementary Results 4 - close vs distant REC

```{r}

semmst_merged_data_filtered_H4b_REC_clodis = semmst_merged_data_filtered %>% 
  filter(task == "RecognitionRespCloDis") %>% 
  filter(cope_name %in% c("DistantCR", "CloseCR"))

# ASSUMPTION CHECKS
## OUTLIER
semmst_merged_data_filtered_H4b_REC_clodis %>%
  group_by(cope_name, roi_cluster) %>%
  identify_outliers(estimate) %>% 
  dplyr::select(ID, roi_cluster, cope_name, is.outlier, is.extreme) %>% 
  filter(is.extreme==TRUE)

semmst_merged_data_filtered_H4b_REC_clodis_nooutlier = semmst_merged_data_filtered_H4b_REC_clodis %>%
  ungroup()

semmst_merged_H4b_REC_clodis_PWC = semmst_merged_data_filtered_H4b_REC_clodis_nooutlier %>%
  group_by(roi_cluster) %>% 
  pairwise_t_test(
    estimate ~ cope_name, 
    paired = TRUE,
    detailed = TRUE,
    ) %>% 
  ungroup() %>% 
  adjust_pvalue(method = "bonferroni") %>%
  add_significance() %>%
  ungroup() %>% 
  mutate(label = paste0("p=", signif(p.adj, 3)))
semmst_merged_H4b_REC_clodis_PWC


# REP  roi_cluster               estimate .y.      group1  group2     n1    n2 statistic     p    df conf.low conf.high method alternative p.adj 
## 1 L_HEAD_DGCA23_HEAD_SUB_14  -0.110  estimate CloseCR Distan…    30    30     -1.55 0.133    29   -0.255    0.0355 T-test two.sided   0.266 ns         
## 2 R_HEAD_DGCA23_HEAD_SUB_15  -0.0498 estimate CloseCR Distan…    30    30     -1.07 0.294    29   -0.145    0.0455 T-test two.sided   0.588 ns


```

#### Supplementary Figure 5.

```{r}

# BARPLOT
figSI_clodisREC_dodge <- 0.8

figSI_clodisREC_barsum <- Rmisc::summarySEwithin(
  data        = semmst_merged_data_filtered_H4b_REC_clodis,
  measurevar  = "estimate",
  withinvars  = c("cope_name", "roi_cluster"),
  idvar       = "ID",
  na.rm       = TRUE
)

figSI_clodisREC_roi_lab <- semmst_merged_data_filtered_H4_REC_conditions_nooutlier %>%
  distinct(roi_cluster, hemisphere, roi, cluster, voxels) %>%
  mutate(
    roi_label = case_when(
      roi == "HEAD_DGCA23_HEAD_SUB" & hemisphere == "R" ~ "Right DG-CA2/3-SUB",
      roi == "HEAD_DGCA23_HEAD_SUB" & hemisphere == "L" ~ "Left DG-CA2/3-SUB",
      TRUE ~ NA_character_
    )
  ) %>%
  select(roi_cluster, roi_label)

figSI_clodisREC_level_map <- c("CloseCR", "DistantCR")
figSI_clodisREC_level_lab <- c("Close lure",   "Distant lure")

figSI_clodisREC_barsum <- figSI_clodisREC_barsum %>%
  mutate(cope_name = factor(cope_name, levels = figSI_clodisREC_level_map, labels = figSI_clodisREC_level_lab)) %>%
  left_join(figSI_clodisREC_roi_lab, by = "roi_cluster")

figSI_clodisREC_plot <- ggplot(figSI_clodisREC_barsum, aes(x = cope_name, y = estimate, fill = cope_name)) +
  geom_col(position = position_dodge(width = figSI_clodisREC_dodge), width = 0.65) +
  geom_errorbar(
    aes(ymin = estimate - se, ymax = estimate + se),
    position = position_dodge(width = figSI_clodisREC_dodge),
    width = 0.15,
    size = 1.2
  ) +
  facet_wrap(~ roi_label) +
  theme_classic(base_size = 13) +
  labs(x = "Condition during recognition", y = "Mean % signal change") +
  scale_fill_manual(values = c(
    "Close lure" = "#4477AA",
    "Distant lure"   = "#DDCC77"
  )) +
  scale_y_continuous(expand = expansion(mult = c(0.02, 0.12))) +
  custom_theme +
  guides(fill = "none")

figSI_clodisREC_plot 

```

```{r}

text_base_export=40
figSI_clodisREC_plot_export <- figSI_clodisREC_plot +
  theme_classic(base_size = text_base_export) +
  theme(
    axis.text.x  = element_text(size = text_base_export * 0.90, margin = margin(t = 2)),
    axis.text.y  = element_text(size = text_base_export * 0.90),
    axis.title   = element_text(size = text_base_export * 1.05),
    strip.text = element_text(size = text_base_export * 0.95)
  )

ggsave(
  "derivatives/figures/SI_figures/Figure5SI.png",
  plot   = figSI_clodisREC_plot_export,
  width  = 22, height = 14, units = "in",
  dpi    = 300, bg = "white", device = "png"
)

```


### Supplementary Results 5 - Behaviour wo. covariates and outlier

```{r}
semmst_behav_data_rec_LDI_ANOVA = semmst_behav_data_rec_summary %>% 
  dplyr::select(ID, rec_dprime, close_dprime, distant_dprime) %>% 
  gather("dprime_type", "dprime_value", rec_dprime:distant_dprime) %>% 
  mutate(dprime_type = factor(dprime_type, levels = c("close_dprime", "rec_dprime", "distant_dprime"))) %>% 
    left_join(semmst_behav_data_rec_filtered %>%  dplyr::select(ID, age, sex, education, Vocabulary, Digit_Symbol, NonWord_sum) %>% distinct(), by="ID")

semmst_behav_data_rec_LDI_ANCOVA = semmst_behav_data_rec_LDI_ANOVA %>% 
  left_join(semmst_behav_data_rec_filtered %>%  dplyr::select(ID, age, sex, education, Vocabulary, Digit_Symbol, NonWord_sum) %>% distinct(), by="ID") %>%
  mutate(Vocabulary_scale = scale(Vocabulary)) %>% 
  mutate(Digit_Symbol_scale = scale(Digit_Symbol)) %>% 
  mutate(NonWord_sum_scale = scale(NonWord_sum)) %>% drop_na()
 
# ASSUMPTION CHECKS
## OUTLIER
semmst_behav_data_rec_LDI_ANOVA %>%
  group_by(dprime_type) %>%
  identify_outliers(dprime_value)

##NORMALITY
semmst_behav_data_rec_LDI_ANOVA %>% 
  group_by(dprime_type) %>%
  shapiro_test(dprime_value) %>%  print(n=40)

ggqqplot(semmst_behav_data_rec_LDI_ANOVA, "dprime_value", ggtheme = theme_bw()) +
  facet_grid(. ~ dprime_type, labeller = "label_both")


# ANOVA
ANOVA_behav_data_rec_LDI = semmst_behav_data_rec_LDI_ANOVA %>%
  anova_test(dv = dprime_value, wid = ID, within = c(dprime_type), covariate = c(sex, age))

get_anova_table(ANOVA_behav_data_rec_LDI)

# REPORT
## dprime_type   2  54 159.192 2.28e-23     * 0.493

```

#### Supplementary Figure 6.

```{r}
# 1) Prep & adjustment (remove linear effects of covariates)
figSI_outlier_plot_base <- semmst_behav_data_rec_LDI_ANOVA %>%
  filter(!is.na(ID), !is.na(dprime_type), !is.na(dprime_value)) %>%
  mutate(
    dprime_type = factor(dprime_type),
    sex = factor(sex)
  )

# order as: Close, Distant, Target
figSI_outlier_contrast_order <- c("close_dprime", "distant_dprime", "rec_dprime")

# order as: Close, Distant, Target
figSI_outlier_contrast_order <- c("close_dprime", "distant_dprime", "rec_dprime")
figSI_outlier_plot_base <- figSI_outlier_plot_base %>%
  mutate(dprime_type = fct_relevel(dprime_type, figSI_outlier_contrast_order))

# covariate-only model for adjustment
figSI_outlier_mod_cov <- lm(dprime_value ~ sex + age,
              data = figSI_outlier_plot_base)

figSI_outlier_plot_base <- figSI_outlier_plot_base %>%
  mutate(dprime_adj = dprime_value - predict(figSI_outlier_mod_cov, newdata = figSI_outlier_plot_base) + mean(dprime_value, na.rm = TRUE))

# 2) Labels & colors
figSI_outlier_x_lab_map <- c(
  "close_dprime"   = "Close\nlure",
  "distant_dprime" = "Distant\nlure",
  "rec_dprime"  = "Foil"
)

# Paul Tol (muted): blue / yellow / red — CVD-safe, good in print & grayscale
figSI_outlier_fill_vals <- c("close_dprime"="#4477AA", "distant_dprime"="#DDCC77", "rec_dprime"="#117733")

# 3) Plot
behav_figSI_outlier <- ggplot(figSI_outlier_plot_base, aes(x = dprime_type, y = dprime_adj, fill = dprime_type)) +
  geom_boxplot(width = 0.6, outlier.alpha = 0.4, linewidth = 1.8, color = "black") +
  stat_summary(fun = mean, geom = "point", shape = 21,  size = 2.2, fill = "white", color = "black") +
  scale_x_discrete(labels = figSI_outlier_x_lab_map, drop = FALSE) +
  scale_fill_manual(values = figSI_outlier_fill_vals, guide = "none") +
  labs(
    x = "Discriminability contrasts",
    y = "Covariate-adjusted d'\n [p(\"old\"|target) - p(\"old\"|condition)]"
  ) +
  theme_classic(base_size = 14)

behav_figSI_outlier

```

```{r}
behav_figSI_outlier_export <- behav_figSI_outlier +
  theme_classic(base_size = 40) +
  theme(
    axis.title = element_text(size = 42),
    axis.text  = element_text(size = 34)
  ) + labs(x = NULL)

ggsave(
  "derivatives/figures/SI_figures/Figure6SI.png",
  plot   = behav_figSI_outlier_export,
  width  = 16, height = 12, units = "in",
  dpi    = 300,
  bg     = "white",
  device = "png"   # base png
)
```


### Supplementary Results 6 - Encoding wo. covariates and outlier

#### ANOVA

```{r}
# FILTER DATA
semmst_merged_data_H1 = semmst_merged_data_filtered %>% 
  filter(task == "Encoding") %>% 
  filter(cope_name %in% c("LureFirst", "ExactFirst", "LureRepeat", "ExactRepeat")) %>% 
  extract(
    col = cope_name,
    into = c("stim_type", "order"),
    regex = "([A-Za-z]+?)(First|Repeat)$"
  ) %>% 
  mutate(
    stim_type = as.factor(stim_type),
    order = as.factor(order)
  ) %>% 
  mutate(stim_type = factor(stim_type, levels = c("Exact", "Lure")))

# ASSUMPTION CHECKS
## OUTLIER
semmst_merged_data_H1 %>%
  group_by(stim_type, order, roi_cluster) %>%
  identify_outliers(estimate) %>% 
  dplyr::select(ID, is.outlier, is.extreme) %>% 
  filter(is.extreme==TRUE)

semmst_merged_data_H1SI_nooutlier = semmst_merged_data_H1 %>%
  group_by(stim_type, order, roi_cluster) %>%
  #filter(! ID %in% c("sub-434971")) %>%  #, " sub-012421", "sub-632012", "sub-800472")) %>% # c("sub-434971", "sub-982347")) %>%
  ungroup()

##NORMALITY
semmst_merged_data_H1SI_nooutlier %>% 
  group_by(stim_type, order) %>%
  shapiro_test(estimate)

# ANOVA
semmst_merged_data_H1SI_nooutlier_AOV = semmst_merged_data_H1SI_nooutlier %>%
  anova_test(dv = estimate, wid = ID, within = c(stim_type, order, roi_cluster))#, covariate = c(NonWord_sum_scale, Digit_Symbol_scale))

get_anova_table(semmst_merged_data_H1SI_nooutlier_AOV)

# REPORT                       Effect DFn DFd      F        p p<.05      ges
## 1                   stim_type   1  29 16.545 3.33e-04     * 3.30e-02
## 2                       order   1  29 54.775 3.73e-08     * 1.07e-01
## 4             stim_type:order   1  29  4.123 5.20e-02       1.60e-02
```

#### Correlation

```{r}

group_vars_H3SI <- c("ID", "mask_type", "space_type", "contrast", "roi_cluster")

# baseline
semmst_merged_data_H3SI_neural_ps = semmst_merged_data_filtered %>% 
  filter(task %in% c("Encoding")) %>% 
  filter(cope_name %in% c("ExactFirst", "ExactRepeat", "LureFirst","LureRepeat", "CloseFirst", "CloseRepeat", "DistantFirst", "DistantRepeat")) %>% 
  dplyr::select(ID, space_type, cope_name, hemisphere, roi, mask_type, cluster, voxels, contrast, task, roi_cluster, roi_hemisphere, estimate, NonWord_sum_scale, Digit_Symbol_scale, rec_dprime:lure_incorrect) %>% 
  group_by(across(all_of(group_vars_H3SI))) %>%
  pivot_wider(names_from = cope_name, values_from = estimate, values_fill = NA_real_) %>%
  mutate(
    # --- Non-RS bias scores (Exact denominator) ---
    LureBiasScore      = LureRepeat - ExactRepeat, 
    CloseBiasScore     = CloseRepeat - ExactRepeat,
    DistantBiasScore   = DistantRepeat - ExactRepeat
  ) %>%
  ungroup() 

# 1) Filter to the Exact subset and define roi_group
df_corr_input_all_SI <- semmst_merged_data_H3SI_neural_ps %>%
  mutate(roi_group = roi_cluster) %>%
  dplyr::select(ID, roi_group, roi, hemisphere, cluster, voxels, LureBiasScore, lure_dprime, NonWord_sum_scale, Digit_Symbol_scale) %>% 
  ungroup()

df_corr_input_all_SI_nooutlier <- df_corr_input_all_SI %>%
  droplevels() %>% 
  ungroup()

# Fisher-z CI for Pearson r (95% hard-coded)
pearson_ci <- function(r, n) {
  z <- atanh(r)
  se <- 1 / sqrt(n - 3)
  zcrit <- qnorm(1 - (1 - 0.95) / 2)
  c(low = tanh(z - zcrit * se), high = tanh(z + zcrit * se))
}

H3SI_corr_lure_simple <- df_corr_input_all_SI_nooutlier %>%
  group_by(roi_group) %>%
  group_modify(~{
    d_all <- .x

    # Pearson
    d_s  <- d_all %>% dplyr::select(LureBiasScore, lure_dprime) %>% tidyr::drop_na()
    ct_s <- cor.test(d_s$LureBiasScore, d_s$lure_dprime, method = "pearson")

    r_s  <- unname(ct_s$estimate)
    p_s  <- ct_s$p.value
    n_s  <- nrow(d_s)
    ci_s <- pearson_ci(r_s, n_s)

    tibble::tibble(
      n = n_s,
      r = r_s,
      p = p_s,
      ci = sprintf("[%.3f, %.3f]", ci_s["low"], ci_s["high"])
    )
  }) %>%
  ungroup() %>%
  mutate(
    p_adj = p.adjust(p, method = "bonferroni")
  ) %>%
  arrange(p_adj, p)

H3SI_corr_lure_simple

```



#### Supplementary Figure 7B

```{r}
fig_corroutlier_BSI_dodge <- 0.8

fig_corroutlier_BSI_barsum <- Rmisc::summarySEwithin(
  data       = semmst_merged_data_H1SI_nooutlier,
  measurevar = "estimate",
  withinvars = c("stim_type","order","roi_cluster"),
  idvar      = "ID",
  na.rm      = TRUE
) %>%
  mutate(stim_type = factor(as.character(stim_type),
                            levels = c("Exact","Lure"),
                            labels = c("Exact","Modified")))

fig_corroutlier_BSI_roi_lab <- semmst_merged_data_H1SI_nooutlier %>%
  distinct(roi_cluster, hemisphere, roi, cluster, voxels) %>%
  mutate(
    roi_label = case_when(
      roi == "HEAD_DGCA23_HEAD_SUB" & hemisphere == "R" ~ "Right DG-CA2/3-SUB cluster",
      roi == "HEAD_DGCA23_HEAD_SUB" & hemisphere == "L" ~ "Left DG-CA2/3-SUB cluster",
      TRUE ~ as.character(roi_cluster)
    )
  ) %>%
  select(roi_cluster, roi_label)

fig_corroutlier_BSI_barsum <- fig_corroutlier_BSI_barsum %>%
  left_join(fig_corroutlier_BSI_roi_lab, by = "roi_cluster")

# bar plot
fig_corroutlier_BSI <- ggplot(fig_corroutlier_BSI_barsum, aes(
  x = stim_type, y = estimate,
  fill = stim_type,
  group = order
)) +
  geom_col(aes(alpha = order),
           position = position_dodge(width = fig_corroutlier_BSI_dodge),
           width = 0.65) +
  geom_errorbar(
    aes(ymin = estimate - se, ymax = estimate + se),
    position = position_dodge(width = fig_corroutlier_BSI_dodge),
    width = 0.15,
    size = 1.2
  ) +
  facet_wrap(~ roi_label) +
  theme_classic(base_size = 13) +
  labs(x = "Condition during encoding", y = "Mean % signal change", fill = "Stimulus", alpha = "Order") +
  scale_fill_manual(values = c(
    "Exact" = "#66BB6A",
    "Modified"  = "#9575CD"
  )) +
  scale_alpha_manual(values = c(
    "First"  = 0.95,
    "Repeat" = 0.55
  )) +
  scale_y_continuous(expand = expansion(mult = c(0.02, 0.12))) +
  custom_theme +
  guides(fill = "none")

fig_corroutlier_BSI

```



```{r}
text_base_export <- 40

fig_corroutlier_BSI_export <- fig_corroutlier_BSI +
  theme_classic(base_size = text_base_export) +
  theme(
    legend.position = c(0.88, 0.88),
    legend.title = element_text(size = text_base_export * 0.88),
    legend.text  = element_text(size = text_base_export * 0.90),
    axis.text.x  = element_text(size = text_base_export * 0.90, margin = margin(t = 2)),
    axis.text.y  = element_text(size = text_base_export * 0.90),
    axis.title   = element_text(size = text_base_export * 1.05),
    strip.text   = element_blank(),
    panel.spacing.x = unit(4, "in")
  )

ggsave(
  "derivatives/figures/SI_figures/Figure7BSI.png",
  plot   = fig_corroutlier_BSI_export,
  width  = 26, height = 13, units = "in",
  dpi    = 300, bg = "white", device = "png"
)

```


#### Supplementary Figure 7A

```{r}

ID_HI <- "sub-434971"

semmst_merged_data_H1SI_nooutlier_data <- semmst_merged_data_H1SI_nooutlier %>%
  filter(!is.na(estimate)) %>%
  mutate(
    highlight = (ID == ID_HI),

    # Column labels you asked for
    stim_col = case_when(
      stim_type == "Exact" ~ "Exact repeat",
      TRUE                ~ "Modified repeat"   # e.g., Lure -> Modified
    ),

    # Row labels you asked for
    roi_row = case_when(
      str_detect(roi_cluster, "^L$|L")  ~ "Left DG-CA2/3-Subiculum",
      str_detect(roi_cluster, "^R$|R") ~ "Right DG-CA2/3-Subiculum",
      TRUE ~ as.character(roi_cluster)
    ),

    order_row = case_when(
      order == "First"  ~ "First presentation",
      order == "Repeat" ~ "Repeat",
      TRUE ~ as.character(order)
    )
  ) %>%
  mutate(
    stim_col  = factor(stim_col,  levels = c("Exact repeat", "Modified repeat")),
    roi_row   = factor(roi_row,   levels = c("Left DG-CA2/3-Subiculum", "Right DG-CA2/3-Subiculum")),
    order_row = factor(order_row, levels = c("First presentation", "Repeat"))
  )

# compute QQ points per facet (roi_row × order_row × stim_col) ---
semmst_merged_data_H1SI_nooutlier_qq <- semmst_merged_data_H1SI_nooutlier_data %>%
  group_by(roi_row, order_row, stim_col) %>%
  arrange(estimate, .by_group = TRUE) %>%
  mutate(theoretical = qnorm(ppoints(n()))) %>%
  ungroup()

# compute qqline (like R's qqline: through 25% and 75%) per facet ---
semmst_merged_data_H1SI_nooutlier_lines <- semmst_merged_data_H1SI_nooutlier_qq %>%
  group_by(roi_row, order_row, stim_col) %>%
  summarise(
    y25 = quantile(estimate, 0.25, na.rm = TRUE),
    y75 = quantile(estimate, 0.75, na.rm = TRUE),
    x25 = qnorm(0.25),
    x75 = qnorm(0.75),
    slope = (y75 - y25) / (x75 - x25),
    intercept = y25 - slope * x25,
    .groups = "drop"
  )

# plot (thin line, correct highlight, correct labels) ---
fig_corroutlier_SIA_figure = ggplot(semmst_merged_data_H1SI_nooutlier_qq, aes(x = theoretical, y = estimate)) +
  geom_point(size = 2.4, alpha = 0.75, colour = "black") +
  geom_point(
    data = dplyr::filter(semmst_merged_data_H1SI_nooutlier_qq, highlight),
    size = 2.6, alpha = 0.95, colour = "red"
  ) +
  geom_abline(
    data = semmst_merged_data_H1SI_nooutlier_lines,
    aes(slope = slope, intercept = intercept),
    linewidth = 1.2,
    colour = "black"
  ) +
  facet_grid(roi_row + order_row ~ stim_col, labeller = label_value) +
  labs(
    x = "Theoretical quantiles",
    y = "Sample quantiles (% signal change)"
  ) +
  theme_bw()

fig_corroutlier_SIA_figure

```

```{r}

text_base_export <- 34  # tweak (28–40); 34 usually good for dense facet grids

fig_corroutlier_SIA_export <- fig_corroutlier_SIA_figure +
  # bump dot sizes (both black + highlighted red)
  geom_point(size = 7.1, alpha = 0.75, colour = "black") +
  geom_point(
    data = dplyr::filter(semmst_merged_data_H1SI_nooutlier_qq, highlight),
    size = 10.3, alpha = 0.95, colour = "red"
  ) +
  # thicker qqline
  geom_abline(
    data = semmst_merged_data_H1SI_nooutlier_lines,
    aes(slope = slope, intercept = intercept),
    linewidth = 1.6,
    colour = "black"
  ) +
  theme_bw(base_size = text_base_export) +
  theme(
    axis.text.x   = element_text(size = text_base_export * 0.85, margin = margin(t = 6)),
    axis.text.y   = element_text(size = text_base_export * 0.85),
    axis.title.x  = element_text(size = text_base_export * 0.95, margin = margin(t = 10)),
    axis.title.y  = element_text(size = text_base_export * 0.95, margin = margin(r = 10)),
    strip.text    = element_text(size = text_base_export * 0.80, face = "bold"),
    panel.spacing = unit(0.65, "lines"),
    plot.margin   = margin(12, 12, 12, 12)
  )

# install.packages("ragg")
ggsave(
  "derivatives/figures/SI_figures/Figure7ASI.png",
  plot   = fig_corroutlier_SIA_export,
  width  = 16, height = 26, units = "in",
  dpi    = 300, bg = "white", device = ragg::agg_png
)

```


#### Supplementary Figure 7C

```{r}

ID_HI <- "sub-434971"

# 1) Long table (ALL trials only)
fig_corroutlierCSI_df <- df_corr_input_all_SI_nooutlier %>%
  dplyr::select(ID, roi_group, roi, hemisphere, bias = LureBiasScore, lure_dprime) %>%
  tidyr::drop_na(bias, lure_dprime) %>%
  dplyr::mutate(
    hemi_lab = dplyr::recode(hemisphere, L = "Left", R = "Right"),
    roi_clean = roi %>%
      gsub("HEAD_", "", .) %>%
      gsub("_", "-", .) %>%
      gsub("2", "", .),
    facet_lab = paste(hemi_lab, roi_clean)
  )

# 2) Facet labels (no stats)
fig_corroutlierCSI_labs <- fig_corroutlierCSI_df %>%
  dplyr::distinct(roi_group, facet_lab)

# 3) Plot (base)
fig_corroutlierCSI <- ggplot(
  fig_corroutlierCSI_df %>% mutate(highlight = (ID == ID_HI)),
  aes(bias, lure_dprime)
) +
  # all points
  geom_point(
    data = \(d) d %>% filter(!highlight),
    alpha = 0.7, size = 4.5, colour = "grey20"
  ) +
  # highlighted point on top
  geom_point(
    data = \(d) d %>% filter(highlight),
    alpha = 1, size = 6.2, colour = "red"
  ) +
  # regression line (single neutral colour)
  geom_smooth(method = "lm", se = FALSE, linewidth = 1.1, colour = "grey20") +
  facet_wrap(
    ~ roi_group, scales = "free",
    labeller = labeller(roi_group = setNames(fig_corroutlierCSI_labs$facet_lab, fig_corroutlierCSI_labs$roi_group))
  ) +
  labs(
    x = "Modified repeat - exact repeat estimates",
    y = "d' (lures vs targets)"
  ) +
  theme_classic(base_size = 18) +
  custom_theme +
  theme(
    panel.spacing = unit(4, "in")   # big gap like your 6A; reduce if too much
  )

fig_corroutlierCSI
```


```{r}
text_base_export <- 40

fig_corroutlierCSI_export <- fig_corroutlierCSI +
  theme_classic(base_size = text_base_export) +
  theme(
    axis.text.x  = element_text(size = text_base_export * 0.90, margin = margin(t = 2)),
    axis.text.y  = element_text(size = text_base_export * 0.90),
    axis.title   = element_text(size = text_base_export * 1.05),
    panel.spacing = unit(4, "in"),
    strip.text = element_blank()
  ) +
  # make the line thicker for export (optional)
  geom_smooth(method = "lm", se = FALSE, linewidth = 2.6, colour = "grey20")

ggsave(
  "derivatives/figures/SI_figures/Figure7CSI.png",
  plot   = fig_corroutlierCSI_export,
  width  = 26, height = 12, units = "in",
  dpi    = 300, bg = "white", device = "png"
)
```



